### 2025-02-03 uca_radio_eclipse_jurpa.tex
Renaming the .bib file to refs.bib

\documentclass[%
 aip,
% jmp,
% bmf,
% sd,
% rsi,
cp,  % Conference Proceedings
 amsmath,amssymb,%nobibnotes,
% preprint,%
 reprint,%
%author-year,%
%author-numerical,%
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%% Loads a Times-like font. You can also load
%% {newtxtext,newtxtmath}, but not {times}, 
%% {txfonts} nor {mathtpm} as these packages
%% are obsolete and have been known to cause problems.
\usepackage{mathptmx}

\begin{document}

\title{The Title Goes Here with Each Initial Letter Capitalized}% Force line breaks with \\

\author{Author's Name} % Write as First name Surname
 \email[Corresponding author: ]{first.author@insitution.edu}
\author{Author's Name}%
 \email{second.author@institution.edu.}
\affiliation{
  Replace this text with an author's affiliation
  (use complete addresses, including country name or code).% Force line breaks with \\ if necessary
}

\author{Another's Name}
 \email{third.author@anotherinstitution.edu}
\affiliation{%
Second institution and/or address% Force line breaks with \\ if necessary
}%
\affiliation{You would list an author's second affiliation (if applicable) here.}

\date{\today} % It is always \today, today, but any date may be explicitly specified
              % Not printed for conference proceedings

\begin{abstract}
An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article. It is used for
secondary publications and for information retrieval purposes.
\end{abstract}

\maketitle

\section{\label{sec:level1}First-level heading:\protect\\ The line
break was forced \lowercase{via} \textbackslash\textbackslash}

This sample document demonstrates proper use of REV\TeX~4.1 (and
\LaTeXe) in manuscripts prepared for submission to AIP
conference proceedings. Further information can be found in the documentation included in the distribution or available at
\url{http://authors.aip.org} and in the documentation for
REV\TeX~4.1 itself.

When commands are referred to in this example file, they are always
shown with their required arguments, using normal \TeX{} format. In
this format, \verb+#1+, \verb+#2+, etc. stand for required
author-supplied arguments to commands. For example, in
\verb+\section{#1}+ the \verb+#1+ stands for the title text of the
author's section heading, and in \verb+\title{#1}+ the \verb+#1+
stands for the title text of the paper.

Line breaks in section headings at all levels can be introduced using
\textbackslash\textbackslash. A blank input line tells \TeX\ that the
paragraph has ended.

\subsection{\label{sec:level2}Second-level heading: Formatting}

This file may be formatted in both the \texttt{preprint} (the default) and
\texttt{reprint} styles; the latter format may be used to
mimic final journal output. Either format may be used for submission
purposes. Hence, it is essential that authors check that their manuscripts format acceptably
under \texttt{preprint}. Manuscripts submitted to AIP that do not
format correctly under the \texttt{preprint} option may be delayed in
both the editorial and production processes.

\subsubsection{\label{sec:level3}Third-level heading: Citations and Footnotes}

Citations in text refer to entries in the Bibliography;
they use the commands \verb+\cite{#1}+ or \verb+\onlinecite{#1}+.
Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly,
its entire repertoire of commands are available in your document;
see the \verb+natbib+ documentation for further details.
The argument of \verb+\cite+ is a comma-separated list of \emph{keys};
a key may consist of letters and numerals.

By default, citations are numerical; \cite{feyn54} author-year citations are an option.
To give a textual citation, use \verb+\onlinecite{#1}+: (Refs.~\onlinecite{witten2001,epr,Bire82}).
REV\TeX\ ``collapses'' lists of consecutive numerical citations when appropriate.
REV\TeX\ provides the ability to properly punctuate textual citations in author-year style;
this facility works correctly with numerical citations only with \texttt{natbib}'s compress option turned off.
To illustrate, we cite several together \cite{feyn54,witten2001,epr,Berman1983},
and once again (Refs.~\onlinecite{epr,feyn54,Bire82,Berman1983}).
Note that, when numerical citations are used, the references were sorted into the same order they appear in the bibliography.

A reference within the bibliography is specified with a \verb+\bibitem{#1}+ command,
where the argument is the citation key mentioned above.
\verb+\bibitem{#1}+ commands may be crafted by hand or, preferably,
generated by using Bib\TeX.
The AIP styles for REV\TeX~4 include Bib\TeX\ style files
\verb+aipnum.bst+ and \verb+aipauth.bst+, appropriate for
numbered and author-year bibliographies,
respectively.
REV\TeX~4 will automatically choose the style appropriate for
the document's selected class options: the default is numerical, and
you obtain the author-year style by specifying a class option of \verb+author-year+.

This sample file demonstrates a simple use of the Bib\TeX\ tool
via a \verb+\bibliography+ command referencing the \verb+aipsamp.bib+ file.
Running Bib\TeX\ (in this case \texttt{bibtex
aipsamp}) after the first pass of \LaTeX\ produces the file
\verb+aipsamp.bbl+ which contains the automatically formatted
\verb+\bibitem+ commands (including extra markup information via
\verb+\bibinfo+ commands). If not using Bib\TeX, the
\verb+thebibiliography+ environment should be used instead.

\paragraph{Fourth-level heading is run in.}%
Footnotes are produced using the \verb+\footnote{#1}+ command.
Numerical style citations put footnotes into the
bibliography\footnote{Automatically placing footnotes into the bibliography requires using BibTeX to compile the bibliography.}.
Author-year and numerical author-year citation styles (each for its own reason) cannot use this method.
Note: due to the method used to place footnotes in the bibliography, \emph{you
must re-run BibTeX every time you change any of your document's
footnotes}.

\section{Math and Equations}
Inline math may be typeset using the \verb+$+ delimiters. Bold math
symbols may be achieved using the \verb+bm+ package and the
\verb+\bm{#1}+ command it supplies. For instance, a bold $\alpha$ can
be typeset as \verb+$\bm{\alpha}$+ giving $\bm{\alpha}$. Fraktur and
Blackboard (or open face or double struck) characters should be
typeset using the \verb+\mathfrak{#1}+ and \verb+\mathbb{#1}+ commands
respectively. Both are supplied by the \texttt{amssymb} package. For
example, \verb+$\mathbb{R}$+ gives $\mathbb{R}$ and
\verb+$\mathfrak{G}$+ gives $\mathfrak{G}$

In \LaTeX\ there are many different ways to display equations, and a
few preferred ways are noted below. Displayed math will center by
default. Use the class option \verb+fleqn+ to flush equations left.

Below we have numbered single-line equations, the most common kind:
\begin{eqnarray}
\chi_+(p)\alt{\bf [}2|{\bf p}|(|{\bf p}|+p_z){\bf ]}^{-1/2}
\left(
\begin{array}{c}
|{\bf p}|+p_z\\
px+ip_y
\end{array}\right)\;,
\\
\left\{%
 \openone234567890abc123\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}%
\label{eq:one}.
\end{eqnarray}
Note the open one in Eq.~(\ref{eq:one}).

Not all numbered equations will fit within the text width this
way. The equation number will move down automatically if it cannot fit
on the same line with a one-line equation:
\begin{equation}
\left\{
 ab12345678abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}\left(1234567890abcdefghijklmnopqrstuvwxyz123456789\right).
\end{equation}

When the \verb+\label{#1}+ command is used [cf. input for
Eq.~(\ref{eq:one})], the equation can be referred to in text without
knowing the equation number that \TeX\ will assign to it. Just
use \verb+\ref{#1}+, where \verb+#1+ is the same name that used in
the \verb+\label{#1}+ command.

Unnumbered single-line equations can be typeset
using the \verb+\[+, \verb+\]+ format:
\[g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
q^+g^+g^+ \dots ~. \]

\subsection{Multiline equations}

Multiline equations are obtained by using the \verb+eqnarray+
environment.  Use the \verb+\nonumber+ command at the end of each line
to avoid assigning a number:
\begin{eqnarray}
{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
\delta_{\sigma_1,-\sigma_2}
(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
&&\times
[\epsilon_jl_i\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1),
\end{eqnarray}
\begin{eqnarray}
\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
        (N^2-1)\nonumber \\
 & &\times \left( \sum_{i<j}\right)
  \sum_{\text{perm}}
 \frac{1}{S_{12}}
 \frac{1}{S_{12}}
 \sum_\tau c^f_\tau~.
\end{eqnarray}
\textbf{Note:} Do not use \verb+\label{#1}+ on a line of a multiline
equation if \verb+\nonumber+ is also used on that line. Incorrect
cross-referencing will result. Notice the use \verb+\text{#1}+ for
using a Roman font within a math environment.

To set a multiline equation without \emph{any} equation
numbers, use the \verb+\begin{eqnarray*}+,
\verb+\end{eqnarray*}+ format:
\begin{eqnarray*}
\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
        (N^2-1)\\
 & &\times \left( \sum_{i<j}\right)
 \left(
  \sum_{\text{perm}}\frac{1}{S_{12}S_{23}S_{n1}}
 \right)
 \frac{1}{S_{12}}~.
\end{eqnarray*}
To obtain numbers not normally produced by the automatic numbering,
use the \verb+\tag{#1}+ command, where \verb+#1+ is the desired
equation number. For example, to get an equation number of
(\ref{eq:mynum}),
\begin{equation}
g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
q^+g^+g^+ \dots ~. \tag{5.1$'$}\label{eq:mynum}
\end{equation}

A few notes on \verb=\tag{#1}=. \verb+\tag{#1}+ requires
\texttt{amsmath}. The \verb+\tag{#1}+ must come before the
\verb+\label{#1}+, if any. The numbering set with \verb+\tag{#1}+ is
\textit{transparent} to the automatic numbering in REV\TeX{};
therefore, the number must be known ahead of time, and it must be
manually adjusted if other equations are added. \verb+\tag{#1}+ works
with both single-line and multiline equations. \verb+\tag{#1}+ should
only be used in exceptional case - do not use it to number all
equations in a paper.

Enclosing single-line and multiline equations in
\verb+\begin{subequations}+ and \verb+\end{subequations}+ will produce
a set of equations that are ``numbered'' with letters, as shown in
Eqs.~(\ref{subeq:1}) and (\ref{subeq:2}) below:
\begin{subequations}
\label{eq:whole}
\begin{equation}
\left\{
 abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}
\right\},\label{subeq:1}
\end{equation}
\begin{eqnarray}
{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
&&\times
[\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1).\label{subeq:2}
\end{eqnarray}
\end{subequations}
Putting a \verb+\label{#1}+ command right after the
\verb+\begin{subequations}+, allows one to
reference all the equations in a subequations environment. For
example, the equations in the preceding subequations environment were
Eqs.~(\ref{eq:whole}).

\section{Cross-referencing}
REV\TeX{} will automatically number sections, equations, figure
captions, and tables. In order to reference them in text, use the
\verb+\label{#1}+ and \verb+\ref{#1}+ commands. To reference a
particular page, use the \verb+\pageref{#1}+ command.

The \verb+\label{#1}+ should appear in a section heading, within an
equation, or in a table or figure caption. The \verb+\ref{#1}+ command
is used in the text where the citation is to be displayed.  Some
examples: Section~\ref{sec:level1} on page~\pageref{sec:level1},
Table~\ref{tab:table1},%
\begin{table}
\caption{\label{tab:table1}This table illustrates left-aligned, centered,
and right-aligned columns. Note that REV\TeX~4 adjusts the
intercolumn spacing so that the table fills the entire width of the text.
Table captions are numbered automatically.  }
\begin{ruledtabular}
\begin{tabular}{lcr}
Left\footnote{Note a.}&Centered\footnote{Note b.}&Right\\
\hline
1 & 2 & 3\\
10 & 20 & 30\\
100 & 200 & 300\\
\end{tabular}
\end{ruledtabular}
\end{table}
and Fig.~\ref{fig:epsart}.

\section{Figures and Tables}
Figures and tables are typically ``floats''; \LaTeX\ determines their
final position via placement rules.
\LaTeX\ isn't always successful in automatically placing floats where you wish them.

Figures are marked up with the \texttt{figure} environment, the content of which
imports the image (\verb+\includegraphics+) followed by the figure caption (\verb+\caption+).
The argument of the latter command should itself contain a \verb+\label+ command if you
wish to refer to your figure with \verb+\ref+.

Import your image using either the \texttt{graphics} or
\texttt{graphicx} packages. Both of these packages define the
\verb+\includegraphics{#1}+ command, but they differ in the optional
arguments for specifying the orientation, scaling, and translation of the figure.
Fig.~\ref{fig:epsart}%
\begin{figure}
\includegraphics{fig_1}% Here is how to import EPS art
\caption{\label{fig:epsart} A figure caption. The figure captions are
automatically numbered.}
\end{figure}
is an example of this.

The analog of the \texttt{figure} environment is \texttt{table}, which uses
the same \verb+\caption+ command.
However, you should type your caption command first within the \texttt{table},
instead of last as you did for \texttt{figure}.

The heart of any table is the \texttt{tabular} environment,
which represents the table content as a (vertical) sequence of table rows,
each containing a (horizontal) sequence of table cells.
Cells are separated by the \verb+&+ character;
the row terminates with \verb+\\+.
The required argument for the \texttt{tabular} environment
specifies how data are displayed in each of the columns.
For instance, a column
may be centered (\verb+c+), left-justified (\verb+l+), right-justified (\verb+r+),
or aligned on a decimal point (\verb+d+).
(Table~\ref{tab:table4}%
\begin{table}
\caption{\label{tab:table4}Numbers in columns Three--Five have been
aligned by using the ``d'' column specifier (requires the
\texttt{dcolumn} package).
Non-numeric entries (those entries without
a ``.'') in a ``d'' column are aligned on the decimal point.
Use the
``D'' specifier for more complex layouts. }
\begin{ruledtabular}
\begin{tabular}{ccddd}
One&Two&\mbox{Three}&\mbox{Four}&\mbox{Five}\\
\hline
one&two&\mbox{three}&\mbox{four}&\mbox{five}\\
He&2& 2.77234 & 45672. & 0.69 \\
C\footnote{Some tables require footnotes.}
  &C\footnote{Some tables need more than one footnote.}
  & 12537.64 & 37.66345 & 86.37 \\
\end{tabular}
\end{ruledtabular}
\end{table}
illustrates the use of decimal column alignment.)

Extra column-spacing may be be specified as well, although
REV\TeX~4 sets this spacing so that the columns fill the width of the
table.
Horizontal rules are typeset using the \verb+\hline+
command.
The doubled (or Scotch) rules that appear at the top and
bottom of a table can be achieved by enclosing the \texttt{tabular}
environment within a \texttt{ruledtabular} environment.
Rows whose columns span multiple columns can be typeset using \LaTeX's
\verb+\multicolumn{#1}{#2}{#3}+ command
(for example, see the first row of Table~\ref{tab:table3}).%
\begin{table}
\caption{\label{tab:table3}This table demonstrates the use of
\textbackslash\texttt{multicolumn} in rows with entries that span
more than one column.}
\begin{ruledtabular}
\begin{tabular}{ccccc}
 &\multicolumn{2}{c}{$D_{4h}^1$}&\multicolumn{2}{c}{$D_{4h}^5$}\\
 Ion&1st alternative&2nd alternative&lst alternative
&2nd alternative\\ \hline
 K&$(2e)+(2f)$&$(4i)$ &$(2c)+(2d)$&$(4f)$ \\
 Mn&$(2g)$\footnote{The $z$ parameter of these positions is $z\sim\frac{1}{4}$.}
 &$(a)+(b)+(c)+(d)$&$(4e)$&$(2a)+(2b)$\\
 Cl&$(a)+(b)+(c)+(d)$&$(2g)$\footnote{This is a footnote in a table. It is supposed to set on the full width of the page, just as the caption does. }
 &$(4e)^{\text{a}}$\\
 He&$(8r)^{\text{a}}$&$(4j)^{\text{a}}$&$(4g)^{\text{a}}$\\
 Ag& &$(4k)^{\text{a}}$& &$(4h)^{\text{a}}$\\
\end{tabular}
\end{ruledtabular}
\end{table}

The tables in this document illustrate various effects.
Lengthy tables may need to break across pages.
A simple way to allow this is to specify
the \verb+[H]+ float placement on the \texttt{table} environment.
Alternatively, using the standard \LaTeXe\ package \texttt{longtable}
gives more control over how tables break and allows headers and footers
to be specified for each page of the table.
An example of the use of \texttt{longtable} can be found
in the file \texttt{summary.tex} that is included with the REV\TeX~4
distribution.

There are two methods for setting footnotes within a table (these
footnotes will be displayed directly below the table rather than at
the bottom of the page or in the bibliography).
The easiest
and preferred method is just to use the \verb+\footnote{#1}+
command. This will automatically enumerate the footnotes with
lowercase roman letters.
However, it is sometimes necessary to have
multiple entries in the table share the same footnote.
In this case,
create the footnotes using
\verb+\footnotemark[#1]+ and \verb+\footnotetext[#1]{#2}+.
\texttt{\#1} is a numeric value.
Each time the same value for \texttt{\#1} is used,
the same mark is produced in the table.
The \verb+\footnotetext[#1]{#2}+ commands are placed after the \texttt{tabular}
environment.
Examine the \LaTeX\ source and output for Tables~\ref{tab:table1} and
\ref{tab:table2}%
\begin{table}
\caption{\label{tab:table2}A table with more columns still fits
properly in a column. Note that several entries share the same
footnote. Inspect the \LaTeX\ input for this table to see
exactly how it is done.}
\begin{ruledtabular}
\begin{tabular}{cccccccc}
 &$r_c$ (\AA)&$r_0$ (\AA)&$\kappa r_0$&
 &$r_c$ (\AA) &$r_0$ (\AA)&$\kappa r_0$\\
\hline
Cu& 0.800 & 14.10 & 2.550 &Sn\footnotemark[1]
& 0.680 & 1.870 & 3.700 \\
Ag& 0.990 & 15.90 & 2.710 &Pb\footnotemark[2]
& 0.450 & 1.930 & 3.760 \\
Au& 1.150 & 15.90 & 2.710 &Ca\footnotemark[3]
& 0.750 & 2.170 & 3.560 \\
Mg& 0.490 & 17.60 & 3.200 &Sr\footnotemark[4]
& 0.900 & 2.370 & 3.720 \\
Zn& 0.300 & 15.20 & 2.970 &Li\footnotemark[2]
& 0.380 & 1.730 & 2.830 \\
Cd& 0.530 & 17.10 & 3.160 &Na\footnotemark[5]
& 0.760 & 2.110 & 3.120 \\
Hg& 0.550 & 17.80 & 3.220 &K\footnotemark[5]
&  1.120 & 2.620 & 3.480 \\
Al& 0.230 & 15.80 & 3.240 &Rb\footnotemark[3]
& 1.330 & 2.800 & 3.590 \\
Ga& 0.310 & 16.70 & 3.330 &Cs\footnotemark[4]
& 1.420 & 3.030 & 3.740 \\
In& 0.460 & 18.40 & 3.500 &Ba\footnotemark[5]
& 0.960 & 2.460 & 3.780 \\
Tl& 0.480 & 18.90 & 3.550 & & & & \\
\end{tabular}
\end{ruledtabular}
\footnotetext[1]{Here's the first, from Ref.~\onlinecite{feyn54}.}
\footnotetext[2]{Here's the second.}
\footnotetext[3]{Here's the third.}
\footnotetext[4]{Here's the fourth.}
\footnotetext[5]{And etc.}
\end{table}
for an illustration.

Sometimes it can be convenient to place multiple narrow figures or tables side-by-side to conserve space and meet any page length requirements for your conference. This can be done using \texttt{minipage} environments within the \texttt{table} or \texttt{figure} environment. Check the \LaTeX\ source and output for Tables~\ref{tab:multiples1}, \ref{tab:multiples2}, and \ref{tab:multiples3}
\begin{table}[tbp]
\begin{minipage}[t]{0.3\textwidth}
    \caption{First narrow table.}
    \label{tab:multiples1}
    \begin{ruledtabular}
    \begin{tabular}{ll}
        Element Symbol & Element Name \\
        \hline
        H & Hydrogen \\
    \end{tabular}
    \end{ruledtabular}
\end{minipage}\hfill%
\begin{minipage}[t]{0.3\textwidth}
    \caption{Second narrow table, set alongside.}
    \label{tab:multiples2}
    \begin{ruledtabular}
    \begin{tabular}{lr}
        Trial & Time (s) \\
        \hline
        1 & 2.42 \\
        2 & 2.46 \\
        3 & 2.41 \\
    \end{tabular}
    \end{ruledtabular}
\end{minipage}\hfill%
\begin{minipage}[t]{0.3\textwidth}
    \caption{Third narrow table, set alongside once again.}
    \label{tab:multiples3}
    \begin{ruledtabular}
    \begin{tabular}{ll}
        Case & Result \\
        \hline
        A & Pass \\
        B & Fail \\
        C & Pass \\
    \end{tabular}
    \end{ruledtabular}
\end{minipage}
\end{table}
for an example of how to do this. The vertical alignment of the \texttt{minipage}s can be adjusted by changing the optional argument to the environment.

All AIP journals require that the initial citation of
figures or tables be in numerical order.
\LaTeX's automatic numbering of floats is your friend here:
just put each \texttt{figure} environment immediately following
its first reference (\verb+\ref+), as we have done in this example file.

\section{Conclusion}

In this section we welcome you to include a summary of the end results of your research.

\begin{acknowledgments}
We wish to acknowledge the support of the author community in using
REV\TeX{}, offering suggestions and encouragement, testing new versions,
\dots.
\end{acknowledgments}

\nocite{*}
\bibliography{refs}% Produces the bibliography via BibTeX.

\end{document}
%
% ****** End of file aipsamp.tex ******

### 2025-02-04 uca_radio_eclipse_jurpa.tex
Updating author names.
I'm adding our names and affiliation.

The affiliation is screwed up in the output PDF because of a quirk
with the way that the AIP template handles commas in the affiliation
field, but that's hopefully something we don't have to mess with.
They can fix that when they typeset the thing for publication.

@@
 
-\title{The Title Goes Here with Each Initial Letter Capitalized}% Force line breaks with \\
+\title{}% Force line breaks with \\
 
-\author{Author's Name} % Write as First name Surname
- \email[Corresponding author: ]{first.author@insitution.edu}
-\author{Author's Name}%
- \email{second.author@institution.edu.}
-\affiliation{
-  Replace this text with an author's affiliation
-  (use complete addresses, including country name or code).% Force line breaks with \\ if necessary
-}
-
-\author{Another's Name}
- \email{third.author@anotherinstitution.edu}
-\affiliation{%
-Second institution and/or address% Force line breaks with \\ if necessary
-}%
-\affiliation{You would list an author's second affiliation (if applicable) here.}
+\author{August Childress} % Write as First name Surname
+\email[Corresponding author: ]{achildress@cub.uca.edu}
+\affiliation{Department of Physics, Astronomy, and Engineering, University of Central Arkansas, Conway, AR 72035, USA}
+\author{Blayne Griffin}%
+\email{bgriffin@cub.uca.edu.}
+\affiliation{Department of Physics, Astronomy, and Engineering, University of Central Arkansas, Conway, AR 72035, USA}
+\author{Jeremy Lusk}
+\email{jlusk@uca.edu}
+\affiliation{Department of Physics, Astronomy, and Engineering, University of Central Arkansas, Conway, AR 72035, USA}
 

### 2025-02-06 sections/abstract.tex
Created a foloder with the different sections to resude clutter on the main file, and added abstract.

We present radio telescope observations of the 08 April 2024 total solar eclipse from the University of 
Central Arkansas campus in Conway, Arkansas using a 2.3-m SPIDER 230C parabolic radio telescope tuned 
to a frequency of 1420 MHz. Observations began approximately 19 minutes before first contact, and ended 
approximately 2.5 minutes after fourth contact, tracking the sun across the sky using a German equatorial 
mount. Our observations show a reduction in relative radio intensity from the beginning of the lightcurve 
to the middle of totality of approximately 70\%. In our current work, we aim to compare this radio 
lightcurve with theoretical lightcurves of the eclipse as observed from our location, as well as a 
relative optical lightcurve derived from the archived livestream of the eclipse broadcast by the 
University of Central Arkansas observatory. Our goal is to compare these observations in order to 
determine the relative size of the optical and radio sun.

### 2025-02-06 uca_radio_eclipse_jurpa.tex
Adding a title (this can be changed later.)
Created a foloder with the different sections to resude clutter on the main file, and added abstract.

@@
 
-\title{}% Force line breaks with \\
+\title{Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.}% Force line breaks with \\
 
@@
 \begin{abstract}
-An article usually includes an abstract, a concise summary of the work
-covered at length in the main body of the article. It is used for
-secondary publications and for information retrieval purposes.
+\input{sections/abstract}
+
 \end{abstract}

### 2025-02-06 sections/experimental.tex
Reformatted the main tex file for customization, and changed the sections to match requirements

\subsection{\label{sec:radio}The Radio Lightcurve}

\subsection{\label{sec:optical}The Optical Lightcurve}

### 2025-02-06 sections/theoretical.tex
Reformatted the main tex file for customization, and changed the sections to match requirements

\subsection{\label{sec:stellarium}Stellarium}

\subsection{\label{sec:theoreticalLightcurves}Theoretical Lightcurve Comparison}

### 2025-02-06 uca_radio_eclipse_jurpa.tex
Reformatted the main tex file for customization, and changed the sections to match requirements

@@
 \input{sections/abstract}
-
 \end{abstract}
@@
 
-\section{\label{sec:level1}First-level heading:\protect\\ The line
-break was forced \lowercase{via} \textbackslash\textbackslash}
+\section{\label{sec:introduction}Introduction}
+\input{sections/introduction}
 
-This sample document demonstrates proper use of REV\TeX~4.1 (and
-\LaTeXe) in manuscripts prepared for submission to AIP
-conference proceedings. Further information can be found in the documentation included in the distribution or available at
-\url{http://authors.aip.org} and in the documentation for
-REV\TeX~4.1 itself.
+\section{\label{sec:experimental}Experimental Investigations}
+\input{sections/experimental}
 
-When commands are referred to in this example file, they are always
-shown with their required arguments, using normal \TeX{} format. In
-this format, \verb+#1+, \verb+#2+, etc. stand for required
-author-supplied arguments to commands. For example, in
-\verb+\section{#1}+ the \verb+#1+ stands for the title text of the
-author's section heading, and in \verb+\title{#1}+ the \verb+#1+
-stands for the title text of the paper.
+\section{\label{sec:theoretical}Theoretical Studies}
+\input{sections/theoretical}
 
-Line breaks in section headings at all levels can be introduced using
-\textbackslash\textbackslash. A blank input line tells \TeX\ that the
-paragraph has ended.
-
-\subsection{\label{sec:level2}Second-level heading: Formatting}
-
-This file may be formatted in both the \texttt{preprint} (the default) and
-\texttt{reprint} styles; the latter format may be used to
-mimic final journal output. Either format may be used for submission
-purposes. Hence, it is essential that authors check that their manuscripts format acceptably
-under \texttt{preprint}. Manuscripts submitted to AIP that do not
-format correctly under the \texttt{preprint} option may be delayed in
-both the editorial and production processes.
-
-\subsubsection{\label{sec:level3}Third-level heading: Citations and Footnotes}
-
-Citations in text refer to entries in the Bibliography;
-they use the commands \verb+\cite{#1}+ or \verb+\onlinecite{#1}+.
-Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly,
-its entire repertoire of commands are available in your document;
-see the \verb+natbib+ documentation for further details.
-The argument of \verb+\cite+ is a comma-separated list of \emph{keys};
-a key may consist of letters and numerals.
-
-By default, citations are numerical; \cite{feyn54} author-year citations are an option.
-To give a textual citation, use \verb+\onlinecite{#1}+: (Refs.~\onlinecite{witten2001,epr,Bire82}).
-REV\TeX\ ``collapses'' lists of consecutive numerical citations when appropriate.
-REV\TeX\ provides the ability to properly punctuate textual citations in author-year style;
-this facility works correctly with numerical citations only with \texttt{natbib}'s compress option turned off.
-To illustrate, we cite several together \cite{feyn54,witten2001,epr,Berman1983},
-and once again (Refs.~\onlinecite{epr,feyn54,Bire82,Berman1983}).
-Note that, when numerical citations are used, the references were sorted into the same order they appear in the bibliography.
-
-A reference within the bibliography is specified with a \verb+\bibitem{#1}+ command,
-where the argument is the citation key mentioned above.
-\verb+\bibitem{#1}+ commands may be crafted by hand or, preferably,
-generated by using Bib\TeX.
-The AIP styles for REV\TeX~4 include Bib\TeX\ style files
-\verb+aipnum.bst+ and \verb+aipauth.bst+, appropriate for
-numbered and author-year bibliographies,
-respectively.
-REV\TeX~4 will automatically choose the style appropriate for
-the document's selected class options: the default is numerical, and
-you obtain the author-year style by specifying a class option of \verb+author-year+.
-
-This sample file demonstrates a simple use of the Bib\TeX\ tool
-via a \verb+\bibliography+ command referencing the \verb+aipsamp.bib+ file.
-Running Bib\TeX\ (in this case \texttt{bibtex
-aipsamp}) after the first pass of \LaTeX\ produces the file
-\verb+aipsamp.bbl+ which contains the automatically formatted
-\verb+\bibitem+ commands (including extra markup information via
-\verb+\bibinfo+ commands). If not using Bib\TeX, the
-\verb+thebibiliography+ environment should be used instead.
-
-\paragraph{Fourth-level heading is run in.}%
-Footnotes are produced using the \verb+\footnote{#1}+ command.
-Numerical style citations put footnotes into the
-bibliography\footnote{Automatically placing footnotes into the bibliography requires using BibTeX to compile the bibliography.}.
-Author-year and numerical author-year citation styles (each for its own reason) cannot use this method.
-Note: due to the method used to place footnotes in the bibliography, \emph{you
-must re-run BibTeX every time you change any of your document's
-footnotes}.
-
-\section{Math and Equations}
-Inline math may be typeset using the \verb+$+ delimiters. Bold math
-symbols may be achieved using the \verb+bm+ package and the
-\verb+\bm{#1}+ command it supplies. For instance, a bold $\alpha$ can
-be typeset as \verb+$\bm{\alpha}$+ giving $\bm{\alpha}$. Fraktur and
-Blackboard (or open face or double struck) characters should be
-typeset using the \verb+\mathfrak{#1}+ and \verb+\mathbb{#1}+ commands
-respectively. Both are supplied by the \texttt{amssymb} package. For
-example, \verb+$\mathbb{R}$+ gives $\mathbb{R}$ and
-\verb+$\mathfrak{G}$+ gives $\mathfrak{G}$
-
-In \LaTeX\ there are many different ways to display equations, and a
-few preferred ways are noted below. Displayed math will center by
-default. Use the class option \verb+fleqn+ to flush equations left.
-
-Below we have numbered single-line equations, the most common kind:
-\begin{eqnarray}
-\chi_+(p)\alt{\bf [}2|{\bf p}|(|{\bf p}|+p_z){\bf ]}^{-1/2}
-\left(
-\begin{array}{c}
-|{\bf p}|+p_z\\
-px+ip_y
-\end{array}\right)\;,
-\\
-\left\{%
- \openone234567890abc123\alpha\beta\gamma\delta1234556\alpha\beta
- \frac{1\sum^{a}_{b}}{A^2}%
-\right\}%
-\label{eq:one}.
-\end{eqnarray}
-Note the open one in Eq.~(\ref{eq:one}).
-
-Not all numbered equations will fit within the text width this
-way. The equation number will move down automatically if it cannot fit
-on the same line with a one-line equation:
-\begin{equation}
-\left\{
- ab12345678abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
- \frac{1\sum^{a}_{b}}{A^2}%
-\right\}\left(1234567890abcdefghijklmnopqrstuvwxyz123456789\right).
-\end{equation}
-
-When the \verb+\label{#1}+ command is used [cf. input for
-Eq.~(\ref{eq:one})], the equation can be referred to in text without
-knowing the equation number that \TeX\ will assign to it. Just
-use \verb+\ref{#1}+, where \verb+#1+ is the same name that used in
-the \verb+\label{#1}+ command.
-
-Unnumbered single-line equations can be typeset
-using the \verb+\[+, \verb+\]+ format:
-\[g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
-q^+g^+g^+ \dots ~. \]
-
-\subsection{Multiline equations}
-
-Multiline equations are obtained by using the \verb+eqnarray+
-environment.  Use the \verb+\nonumber+ command at the end of each line
-to avoid assigning a number:
-\begin{eqnarray}
-{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
-\delta_{\sigma_1,-\sigma_2}
-(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
-&&\times
-[\epsilon_jl_i\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1),
-\end{eqnarray}
-\begin{eqnarray}
-\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
-        (N^2-1)\nonumber \\
- & &\times \left( \sum_{i<j}\right)
-  \sum_{\text{perm}}
- \frac{1}{S_{12}}
- \frac{1}{S_{12}}
- \sum_\tau c^f_\tau~.
-\end{eqnarray}
-\textbf{Note:} Do not use \verb+\label{#1}+ on a line of a multiline
-equation if \verb+\nonumber+ is also used on that line. Incorrect
-cross-referencing will result. Notice the use \verb+\text{#1}+ for
-using a Roman font within a math environment.
-
-To set a multiline equation without \emph{any} equation
-numbers, use the \verb+\begin{eqnarray*}+,
-\verb+\end{eqnarray*}+ format:
-\begin{eqnarray*}
-\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
-        (N^2-1)\\
- & &\times \left( \sum_{i<j}\right)
- \left(
-  \sum_{\text{perm}}\frac{1}{S_{12}S_{23}S_{n1}}
- \right)
- \frac{1}{S_{12}}~.
-\end{eqnarray*}
-To obtain numbers not normally produced by the automatic numbering,
-use the \verb+\tag{#1}+ command, where \verb+#1+ is the desired
-equation number. For example, to get an equation number of
-(\ref{eq:mynum}),
-\begin{equation}
-g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
-q^+g^+g^+ \dots ~. \tag{5.1$'$}\label{eq:mynum}
-\end{equation}
-
-A few notes on \verb=\tag{#1}=. \verb+\tag{#1}+ requires
-\texttt{amsmath}. The \verb+\tag{#1}+ must come before the
-\verb+\label{#1}+, if any. The numbering set with \verb+\tag{#1}+ is
-\textit{transparent} to the automatic numbering in REV\TeX{};
-therefore, the number must be known ahead of time, and it must be
-manually adjusted if other equations are added. \verb+\tag{#1}+ works
-with both single-line and multiline equations. \verb+\tag{#1}+ should
-only be used in exceptional case - do not use it to number all
-equations in a paper.
-
-Enclosing single-line and multiline equations in
-\verb+\begin{subequations}+ and \verb+\end{subequations}+ will produce
-a set of equations that are ``numbered'' with letters, as shown in
-Eqs.~(\ref{subeq:1}) and (\ref{subeq:2}) below:
-\begin{subequations}
-\label{eq:whole}
-\begin{equation}
-\left\{
- abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
- \frac{1\sum^{a}_{b}}{A^2}
-\right\},\label{subeq:1}
-\end{equation}
-\begin{eqnarray}
-{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
-(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
-&&\times
-[\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1).\label{subeq:2}
-\end{eqnarray}
-\end{subequations}
-Putting a \verb+\label{#1}+ command right after the
-\verb+\begin{subequations}+, allows one to
-reference all the equations in a subequations environment. For
-example, the equations in the preceding subequations environment were
-Eqs.~(\ref{eq:whole}).
-
-\section{Cross-referencing}
-REV\TeX{} will automatically number sections, equations, figure
-captions, and tables. In order to reference them in text, use the
-\verb+\label{#1}+ and \verb+\ref{#1}+ commands. To reference a
-particular page, use the \verb+\pageref{#1}+ command.
-
-The \verb+\label{#1}+ should appear in a section heading, within an
-equation, or in a table or figure caption. The \verb+\ref{#1}+ command
-is used in the text where the citation is to be displayed.  Some
-examples: Section~\ref{sec:level1} on page~\pageref{sec:level1},
-Table~\ref{tab:table1},%
-\begin{table}
-\caption{\label{tab:table1}This table illustrates left-aligned, centered,
-and right-aligned columns. Note that REV\TeX~4 adjusts the
-intercolumn spacing so that the table fills the entire width of the text.
-Table captions are numbered automatically.  }
-\begin{ruledtabular}
-\begin{tabular}{lcr}
-Left\footnote{Note a.}&Centered\footnote{Note b.}&Right\\
-\hline
-1 & 2 & 3\\
-10 & 20 & 30\\
-100 & 200 & 300\\
-\end{tabular}
-\end{ruledtabular}
-\end{table}
-and Fig.~\ref{fig:epsart}.
-
-\section{Figures and Tables}
-Figures and tables are typically ``floats''; \LaTeX\ determines their
-final position via placement rules.
-\LaTeX\ isn't always successful in automatically placing floats where you wish them.
-
-Figures are marked up with the \texttt{figure} environment, the content of which
-imports the image (\verb+\includegraphics+) followed by the figure caption (\verb+\caption+).
-The argument of the latter command should itself contain a \verb+\label+ command if you
-wish to refer to your figure with \verb+\ref+.
-
-Import your image using either the \texttt{graphics} or
-\texttt{graphicx} packages. Both of these packages define the
-\verb+\includegraphics{#1}+ command, but they differ in the optional
-arguments for specifying the orientation, scaling, and translation of the figure.
-Fig.~\ref{fig:epsart}%
-\begin{figure}
-\includegraphics{fig_1}% Here is how to import EPS art
-\caption{\label{fig:epsart} A figure caption. The figure captions are
-automatically numbered.}
-\end{figure}
-is an example of this.
-
-The analog of the \texttt{figure} environment is \texttt{table}, which uses
-the same \verb+\caption+ command.
-However, you should type your caption command first within the \texttt{table},
-instead of last as you did for \texttt{figure}.
-
-The heart of any table is the \texttt{tabular} environment,
-which represents the table content as a (vertical) sequence of table rows,
-each containing a (horizontal) sequence of table cells.
-Cells are separated by the \verb+&+ character;
-the row terminates with \verb+\\+.
-The required argument for the \texttt{tabular} environment
-specifies how data are displayed in each of the columns.
-For instance, a column
-may be centered (\verb+c+), left-justified (\verb+l+), right-justified (\verb+r+),
-or aligned on a decimal point (\verb+d+).
-(Table~\ref{tab:table4}%
-\begin{table}
-\caption{\label{tab:table4}Numbers in columns Three--Five have been
-aligned by using the ``d'' column specifier (requires the
-\texttt{dcolumn} package).
-Non-numeric entries (those entries without
-a ``.'') in a ``d'' column are aligned on the decimal point.
-Use the
-``D'' specifier for more complex layouts. }
-\begin{ruledtabular}
-\begin{tabular}{ccddd}
-One&Two&\mbox{Three}&\mbox{Four}&\mbox{Five}\\
-\hline
-one&two&\mbox{three}&\mbox{four}&\mbox{five}\\
-He&2& 2.77234 & 45672. & 0.69 \\
-C\footnote{Some tables require footnotes.}
-  &C\footnote{Some tables need more than one footnote.}
-  & 12537.64 & 37.66345 & 86.37 \\
-\end{tabular}
-\end{ruledtabular}
-\end{table}
-illustrates the use of decimal column alignment.)
-
-Extra column-spacing may be be specified as well, although
-REV\TeX~4 sets this spacing so that the columns fill the width of the
-table.
-Horizontal rules are typeset using the \verb+\hline+
-command.
-The doubled (or Scotch) rules that appear at the top and
-bottom of a table can be achieved by enclosing the \texttt{tabular}
-environment within a \texttt{ruledtabular} environment.
-Rows whose columns span multiple columns can be typeset using \LaTeX's
-\verb+\multicolumn{#1}{#2}{#3}+ command
-(for example, see the first row of Table~\ref{tab:table3}).%
-\begin{table}
-\caption{\label{tab:table3}This table demonstrates the use of
-\textbackslash\texttt{multicolumn} in rows with entries that span
-more than one column.}
-\begin{ruledtabular}
-\begin{tabular}{ccccc}
- &\multicolumn{2}{c}{$D_{4h}^1$}&\multicolumn{2}{c}{$D_{4h}^5$}\\
- Ion&1st alternative&2nd alternative&lst alternative
-&2nd alternative\\ \hline
- K&$(2e)+(2f)$&$(4i)$ &$(2c)+(2d)$&$(4f)$ \\
- Mn&$(2g)$\footnote{The $z$ parameter of these positions is $z\sim\frac{1}{4}$.}
- &$(a)+(b)+(c)+(d)$&$(4e)$&$(2a)+(2b)$\\
- Cl&$(a)+(b)+(c)+(d)$&$(2g)$\footnote{This is a footnote in a table. It is supposed to set on the full width of the page, just as the caption does. }
- &$(4e)^{\text{a}}$\\
- He&$(8r)^{\text{a}}$&$(4j)^{\text{a}}$&$(4g)^{\text{a}}$\\
- Ag& &$(4k)^{\text{a}}$& &$(4h)^{\text{a}}$\\
-\end{tabular}
-\end{ruledtabular}
-\end{table}
-
-The tables in this document illustrate various effects.
-Lengthy tables may need to break across pages.
-A simple way to allow this is to specify
-the \verb+[H]+ float placement on the \texttt{table} environment.
-Alternatively, using the standard \LaTeXe\ package \texttt{longtable}
-gives more control over how tables break and allows headers and footers
-to be specified for each page of the table.
-An example of the use of \texttt{longtable} can be found
-in the file \texttt{summary.tex} that is included with the REV\TeX~4
-distribution.
-
-There are two methods for setting footnotes within a table (these
-footnotes will be displayed directly below the table rather than at
-the bottom of the page or in the bibliography).
-The easiest
-and preferred method is just to use the \verb+\footnote{#1}+
-command. This will automatically enumerate the footnotes with
-lowercase roman letters.
-However, it is sometimes necessary to have
-multiple entries in the table share the same footnote.
-In this case,
-create the footnotes using
-\verb+\footnotemark[#1]+ and \verb+\footnotetext[#1]{#2}+.
-\texttt{\#1} is a numeric value.
-Each time the same value for \texttt{\#1} is used,
-the same mark is produced in the table.
-The \verb+\footnotetext[#1]{#2}+ commands are placed after the \texttt{tabular}
-environment.
-Examine the \LaTeX\ source and output for Tables~\ref{tab:table1} and
-\ref{tab:table2}%
-\begin{table}
-\caption{\label{tab:table2}A table with more columns still fits
-properly in a column. Note that several entries share the same
-footnote. Inspect the \LaTeX\ input for this table to see
-exactly how it is done.}
-\begin{ruledtabular}
-\begin{tabular}{cccccccc}
- &$r_c$ (\AA)&$r_0$ (\AA)&$\kappa r_0$&
- &$r_c$ (\AA) &$r_0$ (\AA)&$\kappa r_0$\\
-\hline
-Cu& 0.800 & 14.10 & 2.550 &Sn\footnotemark[1]
-& 0.680 & 1.870 & 3.700 \\
-Ag& 0.990 & 15.90 & 2.710 &Pb\footnotemark[2]
-& 0.450 & 1.930 & 3.760 \\
-Au& 1.150 & 15.90 & 2.710 &Ca\footnotemark[3]
-& 0.750 & 2.170 & 3.560 \\
-Mg& 0.490 & 17.60 & 3.200 &Sr\footnotemark[4]
-& 0.900 & 2.370 & 3.720 \\
-Zn& 0.300 & 15.20 & 2.970 &Li\footnotemark[2]
-& 0.380 & 1.730 & 2.830 \\
-Cd& 0.530 & 17.10 & 3.160 &Na\footnotemark[5]
-& 0.760 & 2.110 & 3.120 \\
-Hg& 0.550 & 17.80 & 3.220 &K\footnotemark[5]
-&  1.120 & 2.620 & 3.480 \\
-Al& 0.230 & 15.80 & 3.240 &Rb\footnotemark[3]
-& 1.330 & 2.800 & 3.590 \\
-Ga& 0.310 & 16.70 & 3.330 &Cs\footnotemark[4]
-& 1.420 & 3.030 & 3.740 \\
-In& 0.460 & 18.40 & 3.500 &Ba\footnotemark[5]
-& 0.960 & 2.460 & 3.780 \\
-Tl& 0.480 & 18.90 & 3.550 & & & & \\
-\end{tabular}
-\end{ruledtabular}
-\footnotetext[1]{Here's the first, from Ref.~\onlinecite{feyn54}.}
-\footnotetext[2]{Here's the second.}
-\footnotetext[3]{Here's the third.}
-\footnotetext[4]{Here's the fourth.}
-\footnotetext[5]{And etc.}
-\end{table}
-for an illustration.
-
-Sometimes it can be convenient to place multiple narrow figures or tables side-by-side to conserve space and meet any page length requirements for your conference.
-This can be done using \texttt{minipage} environments within the \texttt{table} or \texttt{figure} environment.
-Check the \LaTeX\ source and output for Tables~\ref{tab:multiples1}, \ref{tab:multiples2}, and \ref{tab:multiples3}
-\begin{table}[tbp]
-\begin{minipage}[t]{0.3\textwidth}
-    \caption{First narrow table.}
-    \label{tab:multiples1}
-    \begin{ruledtabular}
-    \begin{tabular}{ll}
-        Element Symbol & Element Name \\
-        \hline
-        H & Hydrogen \\
-    \end{tabular}
-    \end{ruledtabular}
-\end{minipage}\hfill%
-\begin{minipage}[t]{0.3\textwidth}
-    \caption{Second narrow table, set alongside.}
-    \label{tab:multiples2}
-    \begin{ruledtabular}
-    \begin{tabular}{lr}
-        Trial & Time (s) \\
-        \hline
-        1 & 2.42 \\
-        2 & 2.46 \\
-        3 & 2.41 \\
-    \end{tabular}
-    \end{ruledtabular}
-\end{minipage}\hfill%
-\begin{minipage}[t]{0.3\textwidth}
-    \caption{Third narrow table, set alongside once again.}
-    \label{tab:multiples3}
-    \begin{ruledtabular}
-    \begin{tabular}{ll}
-        Case & Result \\
-        \hline
-        A & Pass \\
-        B & Fail \\
-        C & Pass \\
-    \end{tabular}
-    \end{ruledtabular}
-\end{minipage}
-\end{table}
-for an example of how to do this. The vertical alignment of the \texttt{minipage}s can be adjusted by changing the optional argument to the environment.
-
-All AIP journals require that the initial citation of
-figures or tables be in numerical order.
-\LaTeX's automatic numbering of floats is your friend here:
-just put each \texttt{figure} environment immediately following
-its first reference (\verb+\ref+), as we have done in this example file.
-
-\section{Conclusion}
-
-In this section we welcome you to include a summary of the end results of your research.
+\section{\label{sec:conclusion}Conclusion}
+\input{sections/conclusion}
 
 \begin{acknowledgments}
-We wish to acknowledge the support of the author community in using
-REV\TeX{}, offering suggestions and encouragement, testing new versions,
-\dots.
+\input{sections/acknowledgements}
 \end{acknowledgments}

### 2025-02-07 sections/abstract.tex
Reformatted the main tex file for customization, and changed the sections to match requirements
Adding the units package, using \unit[]{} everywhere
This is a way to make numbers with units behave better. Without it,
you can end up in annoying situations where a linebreak happens
between the numbers and the units. This keeps them together, and it
lets you do things like have fractional units like m/s.

@@
-We present radio telescope observations of the 08 April 2024 total solar eclipse from the University of 
-Central Arkansas campus in Conway, Arkansas using a 2.3-m SPIDER 230C parabolic radio telescope tuned 
-to a frequency of 1420 MHz. Observations began approximately 19 minutes before first contact, and ended 
-approximately 2.5 minutes after fourth contact, tracking the sun across the sky using a German equatorial 
-mount. Our observations show a reduction in relative radio intensity from the beginning of the lightcurve 
-to the middle of totality of approximately 70\%. In our current work, we aim to compare this radio 
-lightcurve with theoretical lightcurves of the eclipse as observed from our location, as well as a 
-relative optical lightcurve derived from the archived livestream of the eclipse broadcast by the 
-University of Central Arkansas observatory. Our goal is to compare these observations in order to 
-determine the relative size of the optical and radio sun.
+We present radio telescope observations of the 08 April 2024 total solar eclipse from the University of Central Arkansas campus in Conway, Arkansas using a \unit[2.3]{m} SPIDER 230C parabolic radio telescope tuned to a frequency of \unit[1420]{MHz}.
+Observations began approximately \unit[19]{min} before first contact, and ended approximately \unit[2.5]{min} after fourth contact, tracking the sun across the sky using a German equatorial mount.
+Our observations show a reduction in relative radio intensity from the beginning of the lightcurve to the middle of totality of approximately 70\%.
+In our current work, we aim to compare this radio lightcurve with theoretical lightcurves of the eclipse as observed from our location, as well as a relative optical lightcurve derived from the archived livestream of the eclipse broadcast by the University of Central Arkansas observatory.
+Our goal is to compare these observations in order to determine the relative size of the optical and radio sun.

### 2025-02-07 sections/theoretical.tex
Adding a description of the Stellarium lightcurve

@@
 
+In order to check the validity of our livestream-derived optical lightcurve, we needed a way of finding the expected eclipse obscuration percentage over time for our location.
+We used the free, open-source planetarium software \texttt{Stellarium} to achieve this.
+After setting the time, date and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
+
+The resulting theoretical lightcurve is shown in Figure \ref{fig:livestream_stellarium_comparison}, alongside the eclipse obscruation derived from the UCA Observatory livestream.
+The agreement between the two is excellent, validating our optical eclipse lightcurve.
+
 \subsection{\label{sec:theoreticalLightcurves}Theoretical Lightcurve Comparison}

### 2025-02-11 sections/acknowledgements.tex
I have updated my sections, I hope this works.

\noindent Special thanks to these people for providing us the data necessary for our project:

% Come back and indent and make parentheses affiliations
\begin{enumerate}
    \item Scott Austin, Ph.D. (Director of Astronomical Facilities Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas) 
    \item Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator)
    \item Shane Ayotte. (UCA Mathematics Student)
\end{enumerate}

Technical Specifications of equipment used:
\begin{itemize}
    \item Optical Observations:
    \begin{itemize}
        \item Meade-14 LX200R on a Paramount MX+ equatorial mount
        \item Sony Alpha 6400 camera
        \item Sony FE 24mm-240mm f/3.5-6.3 lens
        \item NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter(Removed during Totality marked by 2460409.2849 JD and 2460409.2884 JD).
    \end{itemize}
    \item Radio Observations:
    \begin{itemize}
        \item Spider 230C: 2.3 meter aluminum dish, tuned to the spin-flip transition of HI at 1429.25 MHz.
        \item Mounted on a SkyWatcher EQ8-R Pro equatorial mount.
    \end{itemize}
\end{itemize}

References% Somehow make this bigger and make it in BibTex

\begin{enumerate}
    \item Stellarium \url{https://stellarium.org/}
    \item Messerotti, M., Zlobec, P., and Padovan, S. (2000). \textit{Radio Polarimetric Observations of the 11 August 1999 Solar Eclipse via the Trieste Solar Radio System.} 463, 595.
    \item \url{https://ssd.jpl.nasa.gov/horizons/}
    \item Leung, C. S., Fok, T. K. T., Hui, K. H. K., Ng, K. W., Lee, C. M., and Chang, S. H. (2022). Solar Eclipse Observations with Small Radio Telescope in Hong Kong in the 21 CM Radio Frequency Band. \textit{Romanian Astronomical Journal}, 32, 35-52.
\end{enumerate}

### 2025-02-11 sections/conclusion.tex
I have updated my sections, I hope this works.

% Add Figure 5: Radio Lightcurve Data Analysis
In figure 5, we can see a comparison between our normalized radio and optical lightcurves.
This comparision clearly shows a difference in brightness during totality, with the optical lightcurves being at 0\% and the radio lightcurve being at 30.9\%.
%In that line, should it be "Being at 0 percent" or would it flow better to say "Reached 0 percent"?
This indicates that the radio solar emission comes from a larger radius than the optical.

% Add Figure 6: Radio Lightcurve Fitting
In Figure 6, we generated theoretical lightcurves for the 2024 eclipse.
% We need to site Stellarium
These theoretical curves assumed different solar radii to model a match of the relative drop in brightness from our radio observations.
In order to produce these lightcurves, we began with the high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System.
Using the angular radii of both the sun and moon along with the angular separation between the two, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the following geometric relationships:
% Add Figure 7: Spheres
% Add Equations

The theoretical lightcurve that best matches the depth of the radio eclipse is $R = 1.27R_s$.
This is consistent with our hypothesis of a larger radio disc than optical.
However, the overall profile of the lightcurve is not well fit by this result, and neither is the expected flat bottom if we assume uniform radio brightness across the surface of the sun.
Our result lies between the results of $R=1.14R_s$ found by Messerottie, et. al. (2000), and $R=1.4R_s$ found by Leung et. al. (2021).
In a future study we will compare these and other results to examine potential sources of uncertainty in the measurements.
% Are the above future plans needed at all?

### 2025-02-11 sections/introduction.tex
I have updated my sections, I hope this works.

Our goal with this project is to determine the size of the radio solar disc by using observations during the April 8th, 2024 Total Solar Eclipse.
This eclipse gave us a unique opportunity to observe the outer atmosphere of the sun without the solar disc overwhelming our ground-based radio telescope. % Check spelling of disc
To accomplish this, we need to determine how much of the solar disc is obscured by the moon during totality in both the optical and radio wavelengths.
We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
To verify these results, we have multiple sources of optical lightcurve data:
\begin{itemize}
    \item Livestream from the UCA Observatory
    \item Broad-spectrum light sensor pointed at the sky, also at UCA
    \item Theoretical lightcurve generated by Stellarium
\end{itemize}% I don't like how much space there is between bullets

### 2025-02-13 sections/experimental.tex
added radio and optical lightcurve sections with a small bit of formatting. Need images and format verification

@@
 \subsection{\label{sec:radio}The Radio Lightcurve}
-
+%Image of Raw Data
+Minimal cloud cover and no sustained winds on the day of the eclipse contributed to a nearly issue free radio lightcurve.
+We addressed 3 sources of error in our project:
+A strong gust of wind pushed the telescope off target for a few seconds.
+An issue with the accuracy of our polar alignment, causing the telescope to be slightly off target by the end of observation.
+Local sources of interference.
+In order for this raw data to be compared to the optical lightcurve, these errors must be addressed.
+A number of data analysis methods were used to do this:
+%%Image of linear adjustment functino being added to raw data?
+\paragraph{Linear Adjustment function}
+The first step in our data analysis is to correct for the tracking error.
+We found average Analog to Digital Unit (ADU) counts for the duration of time after 4th contact and average ADU counts for the same duration of time before 1st contact.
+We then created a linear function that shifts the data at the end of the lightcurve upward and decreases in effect to 0 at 1st contact.
+%Image of smoothing being done to above image?
+\paragraph{Smoothing}
+The next step is to smooth the data.
+Our choice to smooth the data came from the need to reduce noise/random spikes in the data to get a better idea of the shape of the curve.
+We chose to apply a Savitzky-Golay filter to do this.
+%Image of normalization being done to above image?
+\paragraph{Normalization}
+The final step is to normalize the data.
+This is done after smoothing to avoid issues with noise spikes.
+Converting the ADU counts to a relative brightness makes it possible to compare with the optical lightcurves.
+\\
+Now that the raw data has been refined, a neat radio lightcurve of the eclipse remains.
 \subsection{\label{sec:optical}The Optical Lightcurve}
+As a comparison to the radio lightcurve created in the previous section, we have 3 sources of optical lightcurve data: A livestream lightcurve using a solar filter-equipped optical telescope, a Vernier Light Sensor (LS-BTA) pointed straight up at the sky, and a theoretical lightcurve created using the software Stellarum.
+\paragraph{The Theoretical Lightcurve}
+Our comparison lightcurve is a theoretical light curve from the software Stellarium, a free open source planetarium capable of calculating the eclipse magnitude and eclipse percentage from our observing location.
+Using the Stellarium API, we extracted the eclipse percentage at 1000 points in time, from shortly before first contact, to shortly after fourth contact.
+\paragraph{The Livestream Lightcurve}
+The livestream lightcurve was created by grayscaling the image of the eclipse and using Otsu thresholding to only count pixels above a certain value.
+To get the time for each data point, we took an image of the in-video clock at the same time we counted the pixels of the eclipse and used computer vision to recognise the characters in the clock, giving us the time at which the frame was pixel-counted.
+The number of pixels of the solar disk over time can then be normalized to a relative brightness.
+\paragraph{The Light Sensor Lightcurve}
+The light sensor used to collect data during the solar eclipse was the Vernier Light Sensor (LS-BTA) pointed at the sky.
+Dr. Todd Abel and Shane Ayotte provided the light sensor data in the form of a .csv file, which we normalized to relative brightness.
+Because the light sensor data had timestamps included, we used it to confirm the accuracy of our other lightcurves timings.
+\\
+By stacking the lightcurves, we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.
+This implies that our lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun’s radio emission.

### 2025-02-13 sections/theoretical.tex
Adding the section on the theoretical lightcurve
Copied the text and equations from the poster

@@
 \subsection{\label{sec:theoreticalLightcurves}Theoretical Lightcurve Comparison}
+
+In order to determine the apparent radius of the sun at \unit[1420]{MHz}, we can compare our observed radio lightcurve to a theoretical lightcurve where the radius of the sun has been changed.
+
+To accomplish this, we first downloaded high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System.
+Using the angular radii of both the sun and moon along with the angular separation between the two, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the geometric relationships shown in Figure \ref{fig:eclipse_geometry}.
+
+\begin{equation}
+  A_1 = \frac{1}{2}r_{\odot}^2\left(\phi_1 - \sin\phi_1\right)
+\end{equation}
+\begin{equation}
+  A_2 = \frac{1}{2}r_{m}^2\left(\phi_2 - \sin\phi_2\right)
+\end{equation}
+
+\begin{equation}
+  \phi_1 = 2\cos^{-1}\left(\frac{r_{\odot}^2 - r_{m}^2+x^2}{2r_{\odot}x}\right)
+\end{equation}
+\begin{equation}
+  \phi_2 = 2\cos^{-1}\left(\frac{x^2 - r_{\odot}^2 + r_{m}^2}{2r_{m}x}\right)
+\end{equation}
+
+Our best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.

### 2025-02-13 sections/experimental.tex
Edited the zero draft to fix copy-paste bulletpoint issue

@@
 Minimal cloud cover and no sustained winds on the day of the eclipse contributed to a nearly issue free radio lightcurve.
-We addressed 3 sources of error in our project:
-A strong gust of wind pushed the telescope off target for a few seconds.
-An issue with the accuracy of our polar alignment, causing the telescope to be slightly off target by the end of observation.
-Local sources of interference.
+We addressed 3 sources of error in our project: A strong gust of wind pushed the telescope off target for a few seconds, an issue with the accuracy of our polar alignment, causing the telescope to be slightly off target by the end of observation, and local sources of interference.
 In order for this raw data to be compared to the optical lightcurve, these errors must be addressed.

### 2025-02-26 sections/experimental.tex
Added the radio/optical lightcurve comparison graph as well as the png.

@@
 This implies that our lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun’s radio emission.
+\\
+\begin{figure}
+    \includegraphics[width=0.5\textwidth]{figures/radioOpticalComparison}
+    \caption{\label{fig:radioOpticalComparison} A comparison of the smoothed/normalized radio lightcurve and the normalized optical lightcurve generated from the livestream.}
+\end{figure}

### 2025-02-27 sections/conclusion.tex
I edited the conclusion

@@
 % Add Figure 5: Radio Lightcurve Data Analysis
-In figure 5, we can see a comparison between our normalized radio and optical lightcurves.
-This comparision clearly shows a difference in brightness during totality, with the optical lightcurves being at 0\% and the radio lightcurve being at 30.9\%.
-%In that line, should it be "Being at 0 percent" or would it flow better to say "Reached 0 percent"?
-This indicates that the radio solar emission comes from a larger radius than the optical.
+In figure 5, we see a comparison between our normalized radio and optical lightcurves.
+This comparision clearly shows a difference in brightness during totality, with the optical lightcurves reaching 0\% and the radio lightcurve reaching 30.9\%.
+This indicates a difference in radius between the solar emissions from the optical and radio wavelengths.
 
 % Add Figure 6: Radio Lightcurve Fitting
-In Figure 6, we generated theoretical lightcurves for the 2024 eclipse.
-% We need to site Stellarium
-These theoretical curves assumed different solar radii to model a match of the relative drop in brightness from our radio observations.
-In order to produce these lightcurves, we began with the high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System.
-Using the angular radii of both the sun and moon along with the angular separation between the two, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the following geometric relationships:
+To analyze this difference in emission radius, we created theoretical lightcurves.
+These  curves can be found in Figure 6, where we compare several theoretical solar radii with our collected radio data.
+These curves, created using JPL Horizons On-Line Ephemeris System, were made such that they model a match of the relative difference in brightness from our radio observations.
+That difference being 0\% in optical and 30.9\% in radio.
+Using the angular radii of the sun and moon, along with their angular separation between each other, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the following geometric relationships:
 % Add Figure 7: Spheres
@@
 
-The theoretical lightcurve that best matches the depth of the radio eclipse is $R = 1.27R_s$.
-This is consistent with our hypothesis of a larger radio disc than optical.
-However, the overall profile of the lightcurve is not well fit by this result, and neither is the expected flat bottom if we assume uniform radio brightness across the surface of the sun.
+These theoretical curves assume a uniform disc brightness, shown by the flat bottom of the lightcurve.
+This flat bottom is not realistic, as limb darkening is not taken into account and the solar surface is non-uniform.
+However, our result was consistent with our hypothesis: The radio solar emission comes from a larger radius than the optical.
+The theoretical lightcurve that best matches the change in brightness of the radio eclipse is $R = 1.27R_s$.
 Our result lies between the results of $R=1.14R_s$ found by Messerottie, et. al. (2000), and $R=1.4R_s$ found by Leung et. al. (2021).
-In a future study we will compare these and other results to examine potential sources of uncertainty in the measurements.
+In a future study, we will compare these and other results to examine potential sources of uncertainty in the measurements.
 % Are the above future plans needed at all?

### 2025-02-27 sections/introduction.tex
I changed some wording in the Introduction

@@
-Our goal with this project is to determine the size of the radio solar disc by using observations during the April 8th, 2024 Total Solar Eclipse.
-This eclipse gave us a unique opportunity to observe the outer atmosphere of the sun without the solar disc overwhelming our ground-based radio telescope. % Check spelling of disc
-To accomplish this, we need to determine how much of the solar disc is obscured by the moon during totality in both the optical and radio wavelengths.
+Our goal with this project is to determine the size of the radio solar disk by using observations during the April 8th, 2024 Total Solar Eclipse.
+This eclipse gave us a unique opportunity to observe the outer atmosphere of the sun without overwhelming our ground-based radio telescope.
+To accomplish this, we need to determine how much of the solar disk is obscured by the moon during totality in both the optical and radio wavelengths.
 We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.

### 2025-02-28 sections/introduction.tex
Replace bullet list in Introduction with sentences. Improved paragraph flow.

@@
 We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
-To verify these results, we have multiple sources of optical lightcurve data:
-\begin{itemize}
-    \item Livestream from the UCA Observatory
-    \item Broad-spectrum light sensor pointed at the sky, also at UCA
-    \item Theoretical lightcurve generated by Stellarium
-\end{itemize}% I don't like how much space there is between bullets
+To verify these results, we have multiple sources of optical lightcurve data: a livestream from the UCA Observatory, a broad-spectrum light sensor pointed at the sky, and a theoretical lightcurve generated by the software Stellarium.
+Using these data, we can compare the optical and radio lightcurves to determine the relative size of the radio solar disk.

### 2025-03-01 sections/conclusion.tex
Fixed spelling of disk in Conclusion
Greatly changed the Conclusion. I copied what was originally there and kept it if it's needed, but I added that information in a much more concise way in the Theoretical Section instead.

@@
-% Add Figure 5: Radio Lightcurve Data Analysis
-In figure 5, we see a comparison between our normalized radio and optical lightcurves.
-This comparision clearly shows a difference in brightness during totality, with the optical lightcurves reaching 0\% and the radio lightcurve reaching 30.9\%.
-This indicates a difference in radius between the solar emissions from the optical and radio wavelengths.
-
-% Add Figure 6: Radio Lightcurve Fitting
-To analyze this difference in emission radius, we created theoretical lightcurves.
-These  curves can be found in Figure 6, where we compare several theoretical solar radii with our collected radio data.
-These curves, created using JPL Horizons On-Line Ephemeris System, were made such that they model a match of the relative difference in brightness from our radio observations.
-That difference being 0\% in optical and 30.9\% in radio.
-Using the angular radii of the sun and moon, along with their angular separation between each other, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the following geometric relationships:
-% Add Figure 7: Spheres
-% Add Equations
-
-These theoretical curves assume a uniform disc brightness, shown by the flat bottom of the lightcurve.
-This flat bottom is not realistic, as limb darkening is not taken into account and the solar surface is non-uniform.
-However, our result was consistent with our hypothesis: The radio solar emission comes from a larger radius than the optical.
-The theoretical lightcurve that best matches the change in brightness of the radio eclipse is $R = 1.27R_s$.
-Our result lies between the results of $R=1.14R_s$ found by Messerottie, et. al. (2000), and $R=1.4R_s$ found by Leung et. al. (2021).
+Based on our comparison of data from a 2.3 m radio telescope, broad-spectrum light sensor, optical livestream, and theoretical data from Stellarium and JPL Horizons, our hypothesis that the radio solar disk is larger than the optical solar disk is supported.
+This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.
+Our result lies between the results of $R_{\mathrm{1420}} = 1.14 R_{\odot}$ found by Messerottie, et. al. (2000), and $R_{\mathrm{1420}} = 1.4 R_{\odot}$ found by Leung et. al. (2021).
 In a future study, we will compare these and other results to examine potential sources of uncertainty in the measurements.
-% Are the above future plans needed at all?

### 2025-03-01 sections/theoretical.tex
Adding the figure showing the geometry of the eclipse
I'd like to re-make this later on, to match the linewidth and style
of the rest of the document, but for now it will do.
Took some info from the Conclusion and put it here in a better format. I think that we should move the Stellarium info around, but I will wait for input before acting.

@@
 
-The resulting theoretical lightcurve is shown in Figure \ref{fig:livestream_stellarium_comparison}, alongside the eclipse obscruation derived from the UCA Observatory livestream.
+The resulting theoretical lightcurve is shown in Figure \ref{fig:livestream_stellarium_comparison}, alongside the eclipse obscuration derived from the UCA Observatory livestream.
 The agreement between the two is excellent, validating our optical eclipse lightcurve.
+% This figure should include the Livestream, Light Sensor, and Stellarium data.
 
@@
 In order to determine the apparent radius of the sun at \unit[1420]{MHz}, we can compare our observed radio lightcurve to a theoretical lightcurve where the radius of the sun has been changed.
-
 To accomplish this, we first downloaded high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System. 
 Using the angular radii of both the sun and moon along with the angular separation between the two, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the geometric relationships shown in Figure \ref{fig:eclipse_geometry}.
+These relationships are also given by Equations 1 through 4.
+
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{figures/drawing}
+  \caption{\label{fig:eclipse_geometry} The geometric relationships used to calculate the obscuration of the sun.}
+\end{figure}
 
@@
 
-Our best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.
+Using these relationships, we can create theoretical lightcurves for varying solar radii.
+We calculated the obscured area of the solar disk at 2000 points in time during the eclipse.
+Our data found that the radio lightcurve reached a minimum of 30.9\% of the total solar flux during totality, whereas the optical lightcurve reached 0\%.
+Assuming a uniform disk brightness, we created theoretical lightcurves for solar radii ranging from $R = 1.0 R_{\odot}$ to $R = 1.5 R_{\odot}$.
+These theoretical lightcurves, shown in Figure \ref{fig:TheoreticalVsRadio}, helped us match the dip in relative difference in brightness within the radio lightcurve.
+Our model does not take into acount the true non-uniformity of the solar surface, nor does it account for limb darkening.
+We found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.

### 2025-03-01 sections/theoretical.tex
Changed Theoretical Section slightly, adding a little groundwork for when we add more figures.

@@
 Assuming a uniform disk brightness, we created theoretical lightcurves for solar radii ranging from $R = 1.0 R_{\odot}$ to $R = 1.5 R_{\odot}$.
-These theoretical lightcurves, shown in Figure \ref{fig:TheoreticalVsRadio}, helped us match the dip in relative difference in brightness within the radio lightcurve.
+These theoretical lightcurves, shown in Figure \ref{fig:RadiovsTheoretical}, helped us match the dip in relative difference in brightness within the radio lightcurve.
 Our model does not take into acount the true non-uniformity of the solar surface, nor does it account for limb darkening.

### 2025-03-06 sections/acknowledgements.tex
Adding a properly formatted .bib file with our references
I removed the references from the acknowledgements section, and
now everything shows up in the bibliography.

@@
 \end{itemize}
-
-References% Somehow make this bigger and make it in BibTex
-
-\begin{enumerate}
-    \item Stellarium \url{https://stellarium.org/}
-    \item Messerotti, M., Zlobec, P., and Padovan, S. (2000). \textit{Radio Polarimetric Observations of the 11 August 1999 Solar Eclipse via the Trieste Solar Radio System.} 463, 595.
-    \item \url{https://ssd.jpl.nasa.gov/horizons/}
-    \item Leung, C.
-S., Fok, T.
-K.
-T., Hui, K.
-H.
-K., Ng, K.
-W., Lee, C.
-M., and Chang, S.
-H.
-(2022).
-Solar Eclipse Observations with Small Radio Telescope in Hong Kong in the 21 CM Radio Frequency Band.
-\textit{Romanian Astronomical Journal}, 32, 35-52.
-\end{enumerate}

### 2025-03-06 sections/acknowledgements.tex

@@
 \begin{enumerate}
-    \item Scott Austin, Ph.D. (Director of Astronomical Facilities Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas) 
+    \item Scott Austin, Ph.D. (Director of Astronomical Facilities, Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas) 
     \item Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator)

### 2025-03-06 sections/observations.tex
Explained why we need to compare the optical and radio lightcurve in the intro to the optical section

--- 2025-02-26 sections/experimental.tex
@@
 \subsection{\label{sec:optical}The Optical Lightcurve}
-As a comparison to the radio lightcurve created in the previous section, we have 3 sources of optical lightcurve data: A livestream lightcurve using a solar filter-equipped optical telescope, a Vernier Light Sensor (LS-BTA) pointed straight up at the sky, and a theoretical lightcurve created using the software Stellarum.
+We collected optical lightcurve data to compare contact times, the depth of the eclipse, and the shape of the lightcurve to our radio observations.
+Our two sources include a livestream lightcurve using a solar filter-equipped optical telescope, and a Vernier Light Sensor (LS-BTA) pointed straight up at the sky.
 \paragraph{The Theoretical Lightcurve}

### 2025-03-06 sections/observations.tex

@@
 \paragraph{The Theoretical Lightcurve}
-Our comparison lightcurve is a theoretical light curve from the software Stellarium, a free open source planetarium capable of calculating the eclipse magnitude and eclipse percentage from our observing location.
+Our comparison lightcurve is a theoretical lightcurve from the software Stellarium, a free open source planetarium capable of calculating the eclipse magnitude and eclipse percentage from our observing location.
 Using the Stellarium API, we extracted the eclipse percentage at 1000 points in time, from shortly before first contact, to shortly after fourth contact.

### 2025-03-06 sections/theoretical.tex
Added RadiovsTheoretical graph
Removed unused figure and reworded text to not need a figure reference

@@
 After setting the time, date and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
-
-The resulting theoretical lightcurve is shown in Figure \ref{fig:livestream_stellarium_comparison}, alongside the eclipse obscuration derived from the UCA Observatory livestream.
+The resulting theoretical lightcurve is overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
 The agreement between the two is excellent, validating our optical eclipse lightcurve.
-% This figure should include the Livestream, Light Sensor, and Stellarium data.
 
@@
 
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{figures/RadiovsTheoretical.png}
+  \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}
+\end{figure}
+
 Using these relationships, we can create theoretical lightcurves for varying solar radii.

### 2025-03-06 sections/abstract.tex
Updated Abstract with Conclusions

@@
 We present radio telescope observations of the 08 April 2024 total solar eclipse from the University of Central Arkansas campus in Conway, Arkansas using a \unit[2.3]{m} SPIDER 230C parabolic radio telescope tuned to a frequency of \unit[1420]{MHz}.
-Observations began approximately \unit[19]{min} before first contact, and ended approximately \unit[2.5]{min} after fourth contact, tracking the sun across the sky using a German equatorial mount.
-Our observations show a reduction in relative radio intensity from the beginning of the lightcurve to the middle of totality of approximately 70\%.
-In our current work, we aim to compare this radio lightcurve with theoretical lightcurves of the eclipse as observed from our location, as well as a relative optical lightcurve derived from the archived livestream of the eclipse broadcast by the University of Central Arkansas observatory.
-Our goal is to compare these observations in order to determine the relative size of the optical and radio sun.
+Observations began approximately \unit[19]{min} before first contact, and ended approximately \unit[2.5]{min} after fourth contact, continuously tracking the sun across the sky.
+Our radio observations show a reduction in relative intensity from the beginning of the lightcurve to the middle of totality of approximately 70\%, indicating that the apparent size of the radio solar disk was larger than the apparent size of the moon and therefore only partially covered.
+This contrasts with optical data, where the eclipse was total.
+To determine the relative size of the radio solar disk, we compared our observed radio and optical data with theoretical curves where we varied the solar radius.
+From our analyses, we found that the radio solar disk is approximately $R_{\mathrm{1420}} = 1.27 R_{\odot}$.
+This is consistent with previously published results.

### 2025-03-06 sections/observations.tex
Removed theoretical section from optical lightcurve section

@@
 Our two sources include a livestream lightcurve using a solar filter-equipped optical telescope, and a Vernier Light Sensor (LS-BTA) pointed straight up at the sky.
-\paragraph{The Theoretical Lightcurve}
-Our comparison lightcurve is a theoretical lightcurve from the software Stellarium, a free open source planetarium capable of calculating the eclipse magnitude and eclipse percentage from our observing location.
-Using the Stellarium API, we extracted the eclipse percentage at 1000 points in time, from shortly before first contact, to shortly after fourth contact.
 \paragraph{The Livestream Lightcurve}
@@
 The number of pixels of the solar disk over time can then be normalized to a relative brightness.
+We compared this livestream lightcurve to a theoretical lightcurve generated by the software \texttt{Stellarium}\cite{zotti_simulated_2020}, and were happy to see that the livestream and theoretical lightcurves overlap quite well.
 \paragraph{The Light Sensor Lightcurve}

### 2025-03-06 sections/introduction.tex
Added more background to Introduction

@@
-Our goal with this project is to determine the size of the radio solar disk by using observations during the April 8th, 2024 Total Solar Eclipse.
-This eclipse gave us a unique opportunity to observe the outer atmosphere of the sun without overwhelming our ground-based radio telescope.
+Our goal with this project is to determine the size of the sun in the radio frequency by using observations during the April 8th, 2024 Total Solar Eclipse.
+Our radio telescope is specifically focused on the electron spin-flip transition of Hydrogen, which is observed at 1420MHz.
+We collected data in both the optical and radio frequencies, providing a unique opportunity to compare the relative size in the optical and radio spectra.
 To accomplish this, we need to determine how much of the solar disk is obscured by the moon during totality in both the optical and radio wavelengths.
 We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
-To verify these results, we have multiple sources of optical lightcurve data: a livestream from the UCA Observatory, a broad-spectrum light sensor pointed at the sky, and a theoretical lightcurve generated by the software Stellarium.
+To verify these results, we have multiple sources of optical lightcurve data: a livestream from the UCA Observatory, a broad-spectrum light sensor pointed at the sky, and theoretical lightcurves generated with \cite{zotti_simulated_2020} and \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}.
 Using these data, we can compare the optical and radio lightcurves to determine the relative size of the radio solar disk.

### 2025-03-06 sections/theoretical.tex
referenced Stellarium where it is mentioned

@@
 In order to check the validity of our livestream-derived optical lightcurve, we needed a way of finding the expected eclipse obscuration percentage over time for our location.
-We used the free, open-source planetarium software \texttt{Stellarium} to achieve this.
-After setting the time, date and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
+We used the free, open-source planetarium software \texttt{Stellarium}\cite{zotti_simulated_2020} to achieve this.
+After setting the time, date and location of our radio telescope in \texttt{Stellarium}\cite{zotti_simulated_2020}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
 The resulting theoretical lightcurve is overlaid on the eclipse obscuration derived from the UCA Observatory livestream.

### 2025-03-06 sections/observations.tex
Removed mention of .csv file
Added an explenation of what normalization is

--- 2025-03-06 sections/observations.tex
@@
 The final step is to normalize the data.
+Normalization is the process by which the data of a graph is scaled by a constant such that the highest points are equal to 100, essentially making the data a percentage of its highest value.
 This is done after smoothing to avoid issues with noise spikes.
@@
 The number of pixels of the solar disk over time can then be normalized to a relative brightness.
+We compared this livestream lightcurve to a theoretical lightcurve generated by the software \texttt{Stellarium}\cite{zotti_simulated_2020}, and were happy to see that the livestream and theoretical lightcurves overlap quite well.
 \paragraph{The Light Sensor Lightcurve}
 The light sensor used to collect data during the solar eclipse was the Vernier Light Sensor (LS-BTA) pointed at the sky.
-Dr. Todd Abel and Shane Ayotte provided the light sensor data in the form of a .csv file, which we normalized to relative brightness.
+Dr. Todd Abel and Shane Ayotte provided the light sensor data, which we normalized to relative brightness.
 Because the light sensor data had timestamps included, we used it to confirm the accuracy of our other lightcurves timings.

### 2025-03-06 sections/observations.tex
removed comments on the use of figures

--- 2025-03-06 sections/observations.tex
@@
 \subsection{\label{sec:radio}The Radio Lightcurve}
-%Image of Raw Data
 Minimal cloud cover and no sustained winds on the day of the eclipse contributed to a nearly issue free radio lightcurve.
@@
 A number of data analysis methods were used to do this:
-%%Image of linear adjustment functino being added to raw data?
 \paragraph{Linear Adjustment function}
@@
 We then created a linear function that shifts the data at the end of the lightcurve upward and decreases in effect to 0 at 1st contact.
-%Image of smoothing being done to above image?
 \paragraph{Smoothing}
@@
 We chose to apply a Savitzky-Golay filter to do this.
-%Image of normalization being done to above image?
 \paragraph{Normalization}
 The final step is to normalize the data.
+Normalization is the process by which the data of a graph is scaled by a constant such that the highest points are equal to 100, essentially making the data a percentage of its highest value.
 This is done after smoothing to avoid issues with noise spikes.
@@
 The light sensor used to collect data during the solar eclipse was the Vernier Light Sensor (LS-BTA) pointed at the sky.
-Dr. Todd Abel and Shane Ayotte provided the light sensor data in the form of a .csv file, which we normalized to relative brightness.
+Dr. Todd Abel and Shane Ayotte provided the light sensor data, which we normalized to relative brightness.
 Because the light sensor data had timestamps included, we used it to confirm the accuracy of our other lightcurves timings.

### 2025-03-06 sections/observations.tex
Added a bit mor edetail to the smoothing section, and added a reference for savitzky-golay
Added better specs for radio data in Observations.

--- 2025-03-06 sections/observations.tex
@@
 %Image of Raw Data
-Minimal cloud cover and no sustained winds on the day of the eclipse contributed to a nearly issue free radio lightcurve.
-We addressed 3 sources of error in our project: A strong gust of wind pushed the telescope off target for a few seconds, an issue with the accuracy of our polar alignment, causing the telescope to be slightly off target by the end of observation, and local sources of interference.
+Radio Observations took place on April 8th, 2024 at the University of Central Arkansas campus in Conway, Arkansas at approximately 35°04'51"N 92°27'36"W with an elevation of 94 m.
+We began collecting data at 2460409.2186657293 JD and ended at 2460409.3424835186 JD, or 2024-04-08 17:14:53 UTC and 2024-04-08 20:13:11 UTC.
+The telescope used was a Spider 230C radio telescope, a 2.3 m parabolic dish tuned to the electron spin-flip transition of Hydrogen at 1420 MHz.
+During observation, we encountered minimal cloud cover and no sustained winds.
+Despite this, we did have 3 sources of error: A strong gust of wind pushed the telescope off target for a few seconds, an issue with the accuracy of our polar alignment caused the telescope to be slightly off target by the end of observation, and local sources of interference created noise in the data.
 In order for this raw data to be compared to the optical lightcurve, these errors must be addressed.
@@
 The final step is to normalize the data.
-Normalization is the process by which the data of a graph is scaled by a constant such that the highest points are equal to 100, essentially making the data a percentage of its highest value.
 This is done after smoothing to avoid issues with noise spikes.

### 2025-03-06 sections/observations.tex
Checked Observations section bc of weird merge.
Added Optical specs to Observations section

@@
 \paragraph{The Livestream Lightcurve}
-The livestream lightcurve was created by grayscaling the image of the eclipse and using Otsu thresholding to only count pixels above a certain value.
+The livestream of the solar eclipse was created using a Sony Alpha 6400 camera with a Sony FE 24mm-240mm f/3.5-6.3 lens and NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter.
+This solar filter was removed during totality, marked by 2460409.2849 JD and 2460409.2884 JD.
+This setup was attached to a Meade-14 LX200R on a Paramount MX+ equatorial mount for target tracking.
+The lightcurve for this data was created by grayscaling the image of the eclipse and using Otsu thresholding to only count pixels above a certain value.
 To get the time for each data point, we took an image of the in-video clock at the same time we counted the pixels of the eclipse and used computer vision to recognise the characters in the clock, giving us the time at which the frame was pixel-counted.

### 2025-03-06 sections/acknowledgements.tex
Removed Technical Specs from acknowledgements

@@
 \end{enumerate}
-
-Technical Specifications of equipment used:
-\begin{itemize}
-    \item Optical Observations:
-    \begin{itemize}
-        \item Meade-14 LX200R on a Paramount MX+ equatorial mount
-        \item Sony Alpha 6400 camera
-        \item Sony FE 24mm-240mm f/3.5-6.3 lens
-        \item NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter(Removed during Totality marked by 2460409.2849 JD and 2460409.2884 JD).
-    \end{itemize}
-    \item Radio Observations:
-    \begin{itemize}
-        \item Spider 230C: 2.3 meter aluminum dish, tuned to the spin-flip transition of HI at 1429.25 MHz.
-        \item Mounted on a SkyWatcher EQ8-R Pro equatorial mount.
-    \end{itemize}
-\end{itemize}

### 2025-03-07 sections/observations.tex
Added linear adjustment function to likear adjustment section.

@@
 \subsection{\label{sec:radio}The Radio Lightcurve}
-%Image of Raw Data
 Radio Observations took place on April 8th, 2024 at the University of Central Arkansas campus in Conway, Arkansas at approximately 35°04'51"N 92°27'36"W with an elevation of 94 m.
@@
 A number of data analysis methods were used to do this:
-%%Image of linear adjustment functino being added to raw data?
 \paragraph{Linear Adjustment function}
-The first step in our data analysis is to correct for the tracking error.
-We found average Analog to Digital Unit (ADU) counts for the duration of time after 4th contact and average ADU counts for the same duration of time before 1st contact.
-We then created a linear function that shifts the data at the end of the lightcurve upward and decreases in effect to 0 at 1st contact.
-%Image of smoothing being done to above image?
+The first step in our data analysis is to correct for the tracking error caused by the gust of wind.
+We assume that this tracking error caused the radio intensity to decrease linearly with time.
+To create this error correction function, we found the slope between a point ~2 minutes before 1st contact and a point ~2 minutes after 4th contact. 
+The sign was then flipped on the slope and combined with the x value of the point at 1st contact in point slope form in Equation \ref{linear_adjustment_function}.
+This function is added to the lighturve to adjust for the tracking error.
+\begin{equation}\label{linear_adjustment_function}
+Y = 128.4(x-2460409.2318317825)
+\end{equation}
+Where $Y$ is the adjustment value and $X$ is the time coordinate of each data point. 
 \paragraph{Smoothing}
@@
 We chose to apply a Savitzky-Golay filter to do this.
-%Image of normalization being done to above image?
 \paragraph{Normalization}

### 2025-03-07 sections/observations.tex
Added optical lightcurve comparion image

@@
 \\
-By stacking the lightcurves, we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.
+By stacking the lightcurves [\ref{fig:OpticalLightcurveComparison}], we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.
 This implies that our lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun’s radio emission.
@@
 \end{figure}
+\\
+\begin{figure}
+    \includegraphics[width=0.5\textwidth]{figures/OpticalLightcurveComparison}
+    \caption{\label{fig:OpticalLightcurveComparison} A comparison of the livestream, light sensor, and \texttt{Stellarium} lightcurves.}
+\end{figure}

### 2025-03-07 sections/conclusion.tex
Fixed Conclusion Citations
Cleaned up Sections and edited Conclusion I cleaned up general stuff in Observations and Theoretical, including an explanation as to the variance in radio vs theoretical curves. I also edited the conclusion to match these changes.

@@
-Based on our comparison of data from a 2.3 m radio telescope, broad-spectrum light sensor, optical livestream, and theoretical data from Stellarium and JPL Horizons, our hypothesis that the radio solar disk is larger than the optical solar disk is supported.
-This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.
-Our result lies between the results of $R_{\mathrm{1420}} = 1.14 R_{\odot}$ found by Messerottie, et. al. (2000), and $R_{\mathrm{1420}} = 1.4 R_{\odot}$ found by Leung et. al. (2021).
-In a future study, we will compare these and other results to examine potential sources of uncertainty in the measurements.
+Based on our comparison of data from a 2.3 m radio telescope, a broad-spectrum light sensor, an optical livestream, and theoretical data from \texttt{Stellarium}\cite{zotti_simulated_2020} and JPL Horizons \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}, our hypothesis that the radio solar disk is larger than the optical solar disk is supported.
+This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$, lying between the results of other studies \cite{messerotti_radio_2000} and \cite{leung_solar_2022}.
+In future work, we will compare these and other results to examine potential sources of uncertainty in our measurements and apparent variance in data.
+We will also explore different modeling techniques to further characterize the radio emissions from the Sun.

### 2025-03-07 sections/observations.tex
Cleaned up Sections and edited Conclusion I cleaned up general stuff in Observations and Theoretical, including an explanation as to the variance in radio vs theoretical curves. I also edited the conclusion to match these changes.

--- 2025-03-06 sections/observations.tex
@@
 The number of pixels of the solar disk over time can then be normalized to a relative brightness.
-We compared this livestream lightcurve to a theoretical lightcurve generated by the software \texttt{Stellarium}\cite{zotti_simulated_2020}, and were happy to see that the livestream and theoretical lightcurves overlap quite well.
+We compared this livestream lightcurve to a theoretical lightcurve generated by the software \texttt{Stellarium}\cite{zotti_simulated_2020}, and found that the livestream and theoretical lightcurves overlap well.
 \paragraph{The Light Sensor Lightcurve}
@@
 Dr. Todd Abel and Shane Ayotte provided the light sensor data, which we normalized to relative brightness.
-Because the light sensor data had timestamps included, we used it to confirm the accuracy of our other lightcurves timings.
+Because the light sensor data had timestamps included, we used it to confirm the timing accuracy of our other lightcurves.
 \\

### 2025-03-07 sections/theoretical.tex
Adding an in-text citation for JPL ephemeris
removed unnessisary citations
Cleaned up Sections and edited Conclusion I cleaned up general stuff in Observations and Theoretical, including an explanation as to the variance in radio vs theoretical curves. I also edited the conclusion to match these changes.

@@
 After setting the time, date and location of our radio telescope in \texttt{Stellarium}\cite{zotti_simulated_2020}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
-The resulting theoretical lightcurve is overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
+The resulting theoretical lightcurve was then overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
 The agreement between the two is excellent, validating our optical eclipse lightcurve.
+% Shouldn't we have a figure here?
 
@@
 
-In order to determine the apparent radius of the sun at \unit[1420]{MHz}, we can compare our observed radio lightcurve to a theoretical lightcurve where the radius of the sun has been changed.
-To accomplish this, we first downloaded high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System. 
+In order to determine the apparent radius of the sun at \unit[1420]{MHz}, we can compare our observed radio lightcurve to a series of theoretical lightcurves where the radius of the sun has been changed.
+To accomplish this, we first downloaded high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}. 
 Using the angular radii of both the sun and moon along with the angular separation between the two, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the geometric relationships shown in Figure \ref{fig:eclipse_geometry}.
@@
 \end{figure}
-
-Using these relationships, we can create theoretical lightcurves for varying solar radii.
-We calculated the obscured area of the solar disk at 2000 points in time during the eclipse.
 Our data found that the radio lightcurve reached a minimum of 30.9\% of the total solar flux during totality, whereas the optical lightcurve reached 0\%.
-Assuming a uniform disk brightness, we created theoretical lightcurves for solar radii ranging from $R = 1.0 R_{\odot}$ to $R = 1.5 R_{\odot}$.
-These theoretical lightcurves, shown in Figure \ref{fig:RadiovsTheoretical}, helped us match the dip in relative difference in brightness within the radio lightcurve.
-Our model does not take into acount the true non-uniformity of the solar surface, nor does it account for limb darkening.
-We found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.
+Using these relationships, we were able to create theoretical lightcurves for varying solar radii from $R = 1.0 R_{\odot}$ to $R = 1.45 R_{\odot}$ by calculating the obscured area of the solar disk at 2000 points in time during the eclipse.
+These theoretical lightcurves, shown in Figure \ref{fig:RadiovsTheoretical}, helped us match the dip in relative difference in brightness within the radio lightcurve, but it was not a perfect match.
+Although the dip in brightness was accurate, the curves show variance in slope.
+The theoretical curves assume a uniform disk brightness, not accounting for sunspots or other solar activity.
+Nor do they account for limb darkening and how that may change as the obscuration changes throughout the eclipse.
+Despite these variances, we found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.
+This lies between the results of $R_{\mathrm{1420}} = 1.14 R_{\odot}$ found by \cite{messerotti_radio_2000}, and $R_{\mathrm{1420}} = 1.4 R_{\odot}$ found by \cite{leung_solar_2022}.

### 2025-03-11 sections/observations.tex
Editing the observations section.
Mostly cleaning up references to figures and editing the optical
lightcurve section to help motivate why we're using the livestream
to compare with.

@@
 We began collecting data at 2460409.2186657293 JD and ended at 2460409.3424835186 JD, or 2024-04-08 17:14:53 UTC and 2024-04-08 20:13:11 UTC.
-The telescope used was a Spider 230C radio telescope, a 2.3 m parabolic dish tuned to the electron spin-flip transition of Hydrogen at 1420 MHz.
+The telescope used was a Spider 230C radio telescope with a 2.3 m parabolic dish tuned to the electron spin-flip transition of Hydrogen at 1420 MHz.
 During observation, we encountered minimal cloud cover and no sustained winds.
@@
 \paragraph{Linear Adjustment function}
-The first step in our data analysis is to correct for the tracking error caused by the gust of wind.
+The first step in our data analysis is to correct for the tracking error caused by re-targeting the telescope after the gust of wind.
+In our raw radio data, the brightness of the sun after fourth contact is less than the same period just before first contact -- indicating that the telescope was not tracking the sun across the sky perfectly accurately.
 We assume that this tracking error caused the radio intensity to decrease linearly with time.
@@
 Our choice to smooth the data came from the need to reduce noise/random spikes in the data to get a better idea of the shape of the curve.
-We chose to apply a Savitzky-Golay filter to do this.
+We chose to apply a Savitzky-Golay filter \cite{savitzky_golay_1964} to do this.
 \paragraph{Normalization}
@@
 Converting the ADU counts to a relative brightness makes it possible to compare with the optical lightcurves.
-\\
-Now that the raw data has been refined, a neat radio lightcurve of the eclipse remains.
+The smoothed and noramlized data can be seen in Figure \ref{fig:RadioOpticalComparison}.
+
+\begin{figure}[h]
+    \includegraphics[width=0.5\textwidth]{figures/radioOpticalComparison}
+    \caption{\label{fig:RadioOpticalComparison} A comparison of the smoothed/normalized radio lightcurve and the normalized optical lightcurve generated from the livestream.}
+\end{figure}
+
 \subsection{\label{sec:optical}The Optical Lightcurve}
-We collected optical lightcurve data to compare contact times, the depth of the eclipse, and the shape of the lightcurve to our radio observations.
-Our two sources include a livestream lightcurve using a solar filter-equipped optical telescope, and a Vernier Light Sensor (LS-BTA) pointed straight up at the sky.
+
+To better understand the features of our radio data, we need an optical lightcurve for comparison.
+Ideally, the optical lightcurve would be observed from the same location as our radio telescope in order for us to compare contact times, the depth of the eclipse, and the shape of the lightcurve
+Fortunately, Dr. Scott Austin used the UCA observatory across the street from our location to livestream the eclipse using a solar filter-equipped camera connected to the observatory telescope.
+Another experiment near our location led by Dr. Todd Abel and UCA Student Shane Ayotte used a Vernier Light Sensor (LS-BTA) pointed straight up at the sky to measure overall sky brightness.
 \paragraph{The Livestream Lightcurve}
-The livestream of the solar eclipse was created using a Sony Alpha 6400 camera with a Sony FE 24mm-240mm f/3.5-6.3 lens and NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter.
+The livestream of the solar eclipse was captured using a Sony Alpha 6400 camera with a Sony FE 24mm-240mm f/3.5-6.3 lens and NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter.
 This solar filter was removed during totality, marked by 2460409.2849 JD and 2460409.2884 JD.
-This setup was attached to a Meade-14 LX200R on a Paramount MX+ equatorial mount for target tracking.
-The lightcurve for this data was created by grayscaling the image of the eclipse and using Otsu thresholding to only count pixels above a certain value.
+This setup was attached to a Meade-14 LX200R on a Paramount MX+ equatorial mount to track the sun across the sky.
+To transform the livestream into a lightcurve, we needed to extract the percentage of the sun's disk visible in the video frames as the eclipse progressed.
+We accomplished this by first grayscaling the image of the eclipse and then using Otsu thresholding to only count pixels above a certain value.
+This sucessfully counts the bright sun pixels while ignoring the background noise.
 To get the time for each data point, we took an image of the in-video clock at the same time we counted the pixels of the eclipse and used computer vision to recognise the characters in the clock, giving us the time at which the frame was pixel-counted.
 The number of pixels of the solar disk over time can then be normalized to a relative brightness.
-We compared this livestream lightcurve to a theoretical lightcurve generated by the software \texttt{Stellarium}\cite{zotti_simulated_2020}, and found that the livestream and theoretical lightcurves overlap well.
+We compared this livestream lightcurve to a theoretical lightcurve generated by the software \texttt{Stellarium}\cite{zotti_simulated_2020}, and found that the livestream and theoretical lightcurves overlap well, as shown in Figure \ref{fig:OpticalLightcurveComparison}.
 \paragraph{The Light Sensor Lightcurve}
@@
 \\
-By stacking the lightcurves [\ref{fig:OpticalLightcurveComparison}], we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.
-This implies that our lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun’s radio emission.
-\\
-\begin{figure}
-    \includegraphics[width=0.5\textwidth]{figures/radioOpticalComparison}
-    \caption{\label{fig:radioOpticalComparison} A comparison of the smoothed/normalized radio lightcurve and the normalized optical lightcurve generated from the livestream.}
-\end{figure}
-\\
-\begin{figure}
+By stacking the lightcurves as shown in Figure \ref{fig:OpticalLightcurveComparison}, we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.
+This implies that our lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun's radio emission.
+
+\begin{figure}[h]
     \includegraphics[width=0.5\textwidth]{figures/OpticalLightcurveComparison}

### 2025-03-11 sections/theoretical.tex
Editing the theoretial section
Mostly just grouping limb darkening in with the other things that
might be causing our radio data not to line up with the theoretical
models.

@@
 We used the free, open-source planetarium software \texttt{Stellarium}\cite{zotti_simulated_2020} to achieve this.
-After setting the time, date and location of our radio telescope in \texttt{Stellarium}\cite{zotti_simulated_2020}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
+After setting the time, date and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
 The resulting theoretical lightcurve was then overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
-The agreement between the two is excellent, validating our optical eclipse lightcurve.
-% Shouldn't we have a figure here?
+The agreement between the two is excellent, as shown in Figure \ref{fig:OpticalLightcurveComparison}, validating our optical eclipse lightcurve.
 
@@
 
-In order to determine the apparent radius of the sun at \unit[1420]{MHz}, we can compare our observed radio lightcurve to a series of theoretical lightcurves where the radius of the sun has been changed.
+To determine the apparent radius of the sun at \unit[1420]{MHz}, we can compare our observed radio lightcurve to a series of theoretical lightcurves where the radius of the sun has been changed.
 To accomplish this, we first downloaded high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}. 
@@
 \end{figure}
+
 Our data found that the radio lightcurve reached a minimum of 30.9\% of the total solar flux during totality, whereas the optical lightcurve reached 0\%.
 Using these relationships, we were able to create theoretical lightcurves for varying solar radii from $R = 1.0 R_{\odot}$ to $R = 1.45 R_{\odot}$ by calculating the obscured area of the solar disk at 2000 points in time during the eclipse.
-These theoretical lightcurves, shown in Figure \ref{fig:RadiovsTheoretical}, helped us match the dip in relative difference in brightness within the radio lightcurve, but it was not a perfect match.
+These theoretical lightcurves, shown in Figure \ref{fig:RadiovsTheoretical}, helped us match the dip in relative brightness within the radio lightcurve, but it was not a perfect match.
 Although the dip in brightness was accurate, the curves show variance in slope.
-The theoretical curves assume a uniform disk brightness, not accounting for sunspots or other solar activity.
-Nor do they account for limb darkening and how that may change as the obscuration changes throughout the eclipse.
+The theoretical curves assume a uniform disk brightness, not accounting for limb darkening, sunspots, radio emission from the corona, or other solar activity.
 Despite these variances, we found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.

### 2025-03-11 sections/conclusion.tex
Editing the conclusion
I added a little more detail about the things we hope to do in the
future.

--- 2025-03-01 sections/conclusion.tex
@@
-Based on our comparison of data from a 2.3 m radio telescope, broad-spectrum light sensor, optical livestream, and theoretical data from Stellarium and JPL Horizons, our hypothesis that the radio solar disk is larger than the optical solar disk is supported.
-This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.
-Our result lies between the results of $R_{\mathrm{1420}} = 1.14 R_{\odot}$ found by Messerottie, et. al. (2000), and $R_{\mathrm{1420}} = 1.4 R_{\odot}$ found by Leung et. al. (2021).
-In a future study, we will compare these and other results to examine potential sources of uncertainty in the measurements.
+Based on our comparison of data from a 2.3 m radio telescope, a broad-spectrum light sensor, an optical livestream, and theoretical data from \texttt{Stellarium} and JPL Horizons, our hypothesis that the radio solar disk is larger than the optical solar disk is supported.
+This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$, falling between the results of other studies \cite{messerotti_radio_2000} and \cite{leung_solar_2022}.
+In future work, we hope to examine the radio lightcurve in detail, with the goal of mapping radio emission from the sun's surface as features are eclipsed by the moon's edge moving across the face of th sun, as done in \cite{messerotti_radio_2000}.

### 2025-03-13 sections/observations.tex
Added Dr. Austin mention in Livestream section

@@
 \paragraph{The Livestream Lightcurve}
-The livestream of the solar eclipse was captured using a Sony Alpha 6400 camera with a Sony FE 24mm-240mm f/3.5-6.3 lens and NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter.
+The livestream of the solar eclipse was captured by Dr.
+Scott Austin using a Sony Alpha 6400 camera with a Sony FE 24mm-240mm f/3.5-6.3 lens and NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter.
 This solar filter was removed during totality, marked by 2460409.2849 JD and 2460409.2884 JD.

### 2025-03-14 sections/introduction.tex

@@
 We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
-To verify these results, we have multiple sources of optical lightcurve data: a livestream from the UCA Observatory, a broad-spectrum light sensor pointed at the sky, and theoretical lightcurves generated with \cite{zotti_simulated_2020} and \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}.
+In order to compare the radio lightcurve with the visual one, have two sources of optical lightcurve data: a livestream from the UCA Observatory and a broad-spectrum light sensor pointed at the sky.
+We also generated theoretical lightcurves using the software Stellarium \cite{zotti_simulated_2020} and the JPL Horizons On-Line Ephemeris System \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}.
 Using these data, we can compare the optical and radio lightcurves to determine the relative size of the radio solar disk.

### 2025-03-14 sections/acknowledgements.tex
Removed redundant things in acknowledgements
Updating grants section

@@
-\noindent Special thanks to these people for providing us the data necessary for our project:
+\noindent Special thanks to Scott Austin, Ph.D.
+(Director of Astronomical Facilities, Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas), Todd Abel, Ph.D.
+(UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator), and Shane Ayotte.
+(UCA Mathematics Student)
 
-% Come back and indent and make parentheses affiliations
-\begin{enumerate}
-    \item Scott Austin, Ph.D. (Director of Astronomical Facilities, Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas) 
-    \item Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator)
-    \item Shane Ayotte. (UCA Mathematics Student)
-\end{enumerate}
+This research would not have been possible without the support of state and federal research grants.
+Funding to purchase the radio telescope came from the Arkansas Space Grant Consortium (ASGC) Statewide Equipment Award, grant number GR013133-22-UCA.
+Funding to support student research and travel to present our results came from the Arkansas Space Grant Consortium (ASGC) Student Intensive Training award, grant number 242040-25.UCA.SIT.Lusk, a subaward of NASA award number 80NSSC20M0106.

### 2025-03-14 sections/acknowledgements.tex
Updaing the award numbers and adding github links

@@
 (Director of Astronomical Facilities, Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas), Todd Abel, Ph.D.
-(UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator), and Shane Ayotte.
-(UCA Mathematics Student)
+(UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator), and Shane Ayotte (UCA Mathematics Student).
+
+Our research team practices open-source science.
+All data and analysis code can be accessed at \url{https://github.com/UCA-Open-Astronomy-Lab/total_solar_eclipse}.
+The repository for this paper can be found at \url{https://github.com/UCA-Open-Astronomy-Lab/jurpa_eclipse_paper}
 
 This research would not have been possible without the support of state and federal research grants.
-Funding to purchase the radio telescope came from the Arkansas Space Grant Consortium (ASGC) Statewide Equipment Award, grant number GR013133-22-UCA.
-Funding to support student research and travel to present our results came from the Arkansas Space Grant Consortium (ASGC) Student Intensive Training award, grant number 242040-25.UCA.SIT.Lusk, a subaward of NASA award number 80NSSC20M0106.
+Funding to purchase the radio telescope came from the Arkansas Space Grant Consortium (ASGC) Statewide Equipment Award, matched by ASGC state match 20-ARMF-02.
+Funding to support student research and travel to present our results came from the ASGC Student Intensive Training award.
+These ASGC awards are subawards of NASA award number 80NSSC20M0106.

### 2025-03-14 sections/conclusion.tex
Making lots of little tweaks and changes to get us below 4 pages.

@@
 This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$, falling between the results of other studies \cite{messerotti_radio_2000} and \cite{leung_solar_2022}.
-In future work, we hope to examine the radio lightcurve in detail, with the goal of mapping radio emission from the sun's surface as features are eclipsed by the moon's edge moving across the face of th sun, as done in \cite{messerotti_radio_2000}.
+In future work, we hope to examine the radio lightcurve in detail, with the goal of mapping radio emission from the sun's surface as features are eclipsed by the moon's edge moving across the face of the sun, as done in \cite{messerotti_radio_2000}.

### 2025-03-14 sections/observations.tex
Added modified pdf images of graphs from observations
Changed figures to 0.75 textwidth
Making lots of little tweaks and changes to get us below 4 pages.

@@
 \begin{equation}\label{linear_adjustment_function}
-Y = 128.4(x-2460409.2318317825)
+Y = 128.4(t-2460409.2318317825)
 \end{equation}
-Where $Y$ is the adjustment value and $X$ is the time coordinate of each data point. 
+Where $Y$ is the adjustment value and $t$ is the time coordinate of each data point. 
 \paragraph{Smoothing}
@@
 \begin{figure}[h]
-    \includegraphics[width=0.5\textwidth]{figures/radioOpticalComparison}
+  \begin{minipage}{0.495\textwidth}
+    \includegraphics[width=\textwidth]{figures/SNRadioVLivestream}
     \caption{\label{fig:RadioOpticalComparison} A comparison of the smoothed/normalized radio lightcurve and the normalized optical lightcurve generated from the livestream.}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.495\textwidth}
+    \includegraphics[width=\textwidth]{figures/OpticalComparison}
+    \caption{\label{fig:OpticalLightcurveComparison} A comparison of the livestream, light sensor, and \texttt{Stellarium} lightcurves.}
+  \end{minipage}
 \end{figure}
@@
 The number of pixels of the solar disk over time can then be normalized to a relative brightness.
-We compared this livestream lightcurve to a theoretical lightcurve generated by the software \texttt{Stellarium}\cite{zotti_simulated_2020}, and found that the livestream and theoretical lightcurves overlap well, as shown in Figure \ref{fig:OpticalLightcurveComparison}.
 \paragraph{The Light Sensor Lightcurve}
@@
 \\
-By stacking the lightcurves as shown in Figure \ref{fig:OpticalLightcurveComparison}, we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.
+Figure \ref{fig:OpticalLightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}\cite{zotti_simulated_2020}, we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.
 This implies that our lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun's radio emission.
-
-\begin{figure}[h]
-    \includegraphics[width=0.5\textwidth]{figures/OpticalLightcurveComparison}
-    \caption{\label{fig:OpticalLightcurveComparison} A comparison of the livestream, light sensor, and \texttt{Stellarium} lightcurves.}
-\end{figure}

### 2025-03-14 sections/theoretical.tex
Updated RadiovsTheoretical graph
Added minipages to put the equations next to the geometry figure
deleted png version of radiovstheoretical and changed file extention on theoretcial
Changed figures to 0.75 textwidth
Adding equation labels and numbering them
Making lots of little tweaks and changes to get us below 4 pages.

@@
 Using the angular radii of both the sun and moon along with the angular separation between the two, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the geometric relationships shown in Figure \ref{fig:eclipse_geometry}.
-These relationships are also given by Equations 1 through 4.
+These relationships are also given by Equations \ref{eq:geometry_1} through \ref{eq:geometry_4}.
 
 \begin{figure}
-  \includegraphics[width=0.5\textwidth]{figures/drawing}
-  \caption{\label{fig:eclipse_geometry} The geometric relationships used to calculate the obscuration of the sun.}
+\begin{minipage}{0.49\textwidth}
+  \includegraphics[width=0.6\textwidth]{figures/drawing}
+  \caption{\label{fig:eclipse_geometry} The geometric relationships used to calculate the obscuration of the sun.
+The percent obscuration is found by dividing the combined area $A_1 + A_2$ by the apparent area of the sun's disk $\pi r_\odot^2$}
+\end{minipage}
+\hfill
+\begin{minipage}{0.49\textwidth}
+\begin{equation}\label{eq:geometry_1}
+  A_1 = \frac{1}{2}r_{\odot}^2\left(\phi_1 - \sin\phi_1\right)
+\end{equation}
+\begin{equation}\label{eq:geometry_2}
+  A_2 = \frac{1}{2}r_{m}^2\left(\phi_2 - \sin\phi_2\right)
+\end{equation}
+\begin{equation}\label{eq:geometry_3}
+  \phi_1 = 2\cos^{-1}\left(\frac{r_{\odot}^2 - r_{m}^2+x^2}{2r_{\odot}x}\right)
+\end{equation}
+\begin{equation}\label{eq:geometry_4}
+  \phi_2 = 2\cos^{-1}\left(\frac{x^2 - r_{\odot}^2 + r_{m}^2}{2r_{m}x}\right)
+\end{equation}
+\end{minipage}
 \end{figure}
 
-\begin{equation}
-  A_1 = \frac{1}{2}r_{\odot}^2\left(\phi_1 - \sin\phi_1\right)
-\end{equation}
-\begin{equation}
-  A_2 = \frac{1}{2}r_{m}^2\left(\phi_2 - \sin\phi_2\right)
-\end{equation}
-
-\begin{equation}
-  \phi_1 = 2\cos^{-1}\left(\frac{r_{\odot}^2 - r_{m}^2+x^2}{2r_{\odot}x}\right)
-\end{equation}
-\begin{equation}
-  \phi_2 = 2\cos^{-1}\left(\frac{x^2 - r_{\odot}^2 + r_{m}^2}{2r_{m}x}\right)
-\end{equation}
-
 \begin{figure}
-  \includegraphics[width=0.5\textwidth]{figures/RadiovsTheoretical.png}
+  \includegraphics[width=0.75\textwidth]{figures/RadiovsTheoretical}
   \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}
@@
 
-Our data found that the radio lightcurve reached a minimum of 30.9\% of the total solar flux during totality, whereas the optical lightcurve reached 0\%.
-Using these relationships, we were able to create theoretical lightcurves for varying solar radii from $R = 1.0 R_{\odot}$ to $R = 1.45 R_{\odot}$ by calculating the obscured area of the solar disk at 2000 points in time during the eclipse.
+Our data found that the radio lightcurve reached a minimum of 30.9\% of the total solar flux during totality.
+Using these relationships, we were able to create theoretical lightcurves for varying solar radii from $R = 1.0 R_{\odot}$ to $R = 1.45 R_{\odot}$.
 These theoretical lightcurves, shown in Figure \ref{fig:RadiovsTheoretical}, helped us match the dip in relative brightness within the radio lightcurve, but it was not a perfect match.
-Although the dip in brightness was accurate, the curves show variance in slope.
+Although the dip in brightness was accurate, the curves show variance in slope and our radio data does not show the flat bottom expected while the moon transits the larger solar disk.
 The theoretical curves assume a uniform disk brightness, not accounting for limb darkening, sunspots, radio emission from the corona, or other solar activity.

### 2025-03-15 sections/observations.tex
Unding my side-by-side figure, leaving room for new combined figure
We need to replace the figure that's here with the combined figure,
and then update the caption. Then we need to check the references
within the paper to make sure that the ones that refer to the old
figures still make sense when refering to this figure.
Changed Figure references to match new Figure I also fixed a spelling mistake

@@
 Converting the ADU counts to a relative brightness makes it possible to compare with the optical lightcurves.
-The smoothed and noramlized data can be seen in Figure \ref{fig:RadioOpticalComparison}.
+The smoothed and normalized data can be seen in Figure \ref{fig:LightcurveComparison}.
 
+%% Put combined firue here, and adjust width to keep us at 4 pages
 \begin{figure}[h]
-  \begin{minipage}{0.495\textwidth}
-    \includegraphics[width=\textwidth]{figures/SNRadioVLivestream}
-    \caption{\label{fig:RadioOpticalComparison} A comparison of the smoothed/normalized radio lightcurve and the normalized optical lightcurve generated from the livestream.}
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.495\textwidth}
-    \includegraphics[width=\textwidth]{figures/OpticalComparison}
-    \caption{\label{fig:OpticalLightcurveComparison} A comparison of the livestream, light sensor, and \texttt{Stellarium} lightcurves.}
-  \end{minipage}
+    \includegraphics[width=\textwidth]{figures/LightcurveComparison.pdf}
+    \caption{\label{fig:LightcurveComparison} A comparison of the smoothed/normalized radio lightcurve, the normalized optical lightcurve generated from the livestream, the lightcurve generated from the light sensor, and a theoretical lightcurve generated from the software \texttt{Stellarium}.}
 \end{figure}
+
+%\begin{figure}
+%  \includegraphics[width=\textwidth]{figures/OpticalComparison}
+%  \caption{\label{fig:OpticalLightcurveComparison} A comparison of the livestream, light sensor, and \texttt{Stellarium} lightcurves.}
+%\end{figure}
 
@@
 \\
-Figure \ref{fig:OpticalLightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}\cite{zotti_simulated_2020}, we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.
+Figure \ref{fig:LightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}\cite{zotti_simulated_2020}, we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.
 This implies that our lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun's radio emission.

### 2025-03-15 sections/observations.tex
Fixed degree symbols in our lat/long

@@
 \subsection{\label{sec:radio}The Radio Lightcurve}
-Radio Observations took place on April 8th, 2024 at the University of Central Arkansas campus in Conway, Arkansas at approximately 35°04'51"N 92°27'36"W with an elevation of 94 m.
+Radio Observations took place on April 8th, 2024 at the University of Central Arkansas campus in Conway, Arkansas at approximately 35$^\circ$04'51"N 92$^\circ$27'36"W with an elevation of 94 m.
 We began collecting data at 2460409.2186657293 JD and ended at 2460409.3424835186 JD, or 2024-04-08 17:14:53 UTC and 2024-04-08 20:13:11 UTC.

### 2025-03-15 sections/theoretical.tex
Changed Figure references to match new Figure I also fixed a spelling mistake
Updating geometry figure
The text in the figure wasn't filled in, so it looked bad. I've
updated it so that the text looks better
Changed graph sizes to 0.6 to fit.

@@
 The resulting theoretical lightcurve was then overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
-The agreement between the two is excellent, as shown in Figure \ref{fig:OpticalLightcurveComparison}, validating our optical eclipse lightcurve.
+The agreement between the two is excellent, as shown in Figure \ref{fig:LightcurveComparison}, validating our optical eclipse lightcurve.
 
@@
 \begin{minipage}{0.49\textwidth}
-  \includegraphics[width=0.6\textwidth]{figures/drawing}
+  \includegraphics[width=0.6\textwidth]{figures/drawing_updated}
   \caption{\label{fig:eclipse_geometry} The geometric relationships used to calculate the obscuration of the sun.
-The percent obscuration is found by dividing the combined area $A_1 + A_2$ by the apparent area of the sun's disk $\pi r_\odot^2$}
+The percent obscuration is found by dividing the combined area $A_1 + A_2$ by the apparent area of the sun's disk $\pi R_\odot^2$}
 \end{minipage}
@@
 \begin{figure}
-  \includegraphics[width=0.75\textwidth]{figures/RadiovsTheoretical}
+  \includegraphics[width=0.6\textwidth]{figures/RadiovsTheoretical}
   \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}

### 2025-03-15 sections/abstract.tex
A lot of spell and tense checking for uniformity.

@@
 We present radio telescope observations of the 08 April 2024 total solar eclipse from the University of Central Arkansas campus in Conway, Arkansas using a \unit[2.3]{m} SPIDER 230C parabolic radio telescope tuned to a frequency of \unit[1420]{MHz}.
-Observations began approximately \unit[19]{min} before first contact, and ended approximately \unit[2.5]{min} after fourth contact, continuously tracking the sun across the sky.
+Observations began approximately \unit[19]{min} before first contact and ended approximately \unit[2.5]{min} after fourth contact, continuously tracking the sun across the sky.
 Our radio observations show a reduction in relative intensity from the beginning of the lightcurve to the middle of totality of approximately 70\%, indicating that the apparent size of the radio solar disk was larger than the apparent size of the moon and therefore only partially covered.

### 2025-03-15 sections/introduction.tex
A lot of spell and tense checking for uniformity.

@@
 We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
-In order to compare the radio lightcurve with the visual one, have two sources of optical lightcurve data: a livestream from the UCA Observatory and a broad-spectrum light sensor pointed at the sky.
+In order to compare the radio lightcurve with the visual one, we have two sources of optical lightcurve data: a livestream from the UCA Observatory and a broad-spectrum light sensor pointed at the sky.
 We also generated theoretical lightcurves using the software Stellarium \cite{zotti_simulated_2020} and the JPL Horizons On-Line Ephemeris System \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}.

### 2025-03-15 sections/observations.tex
Changed graph sizes to 0.6 to fit.
A lot of spell and tense checking for uniformity.

@@
 The first step in our data analysis is to correct for the tracking error caused by re-targeting the telescope after the gust of wind.
-In our raw radio data, the brightness of the sun after fourth contact is less than the same period just before first contact -- indicating that the telescope was not tracking the sun across the sky perfectly accurately.
+In our raw radio data, the brightness of the sun after fourth contact is less than the same period just before first contact.
+This indicated that the tracking had become inaccurate.
 We assume that this tracking error caused the radio intensity to decrease linearly with time.
-To create this error correction function, we found the slope between a point ~2 minutes before 1st contact and a point ~2 minutes after 4th contact. 
+To create this error correction function, we found the slope between a point around 2 minutes before 1st contact and a point around 2 minutes after 4th contact. 
 The sign was then flipped on the slope and combined with the x value of the point at 1st contact in point slope form in Equation \ref{linear_adjustment_function}.
@@
 \begin{figure}[h]
-    \includegraphics[width=\textwidth]{figures/LightcurveComparison.pdf}
+    \includegraphics[width=0.6\textwidth]{figures/LightcurveComparison.pdf}
     \caption{\label{fig:LightcurveComparison} A comparison of the smoothed/normalized radio lightcurve, the normalized optical lightcurve generated from the livestream, the lightcurve generated from the light sensor, and a theoretical lightcurve generated from the software \texttt{Stellarium}.}
@@
 To better understand the features of our radio data, we need an optical lightcurve for comparison.
-Ideally, the optical lightcurve would be observed from the same location as our radio telescope in order for us to compare contact times, the depth of the eclipse, and the shape of the lightcurve
-Fortunately, Dr. Scott Austin used the UCA observatory across the street from our location to livestream the eclipse using a solar filter-equipped camera connected to the observatory telescope.
+Ideally, the optical lightcurve would be observed from the same location as our radio telescope in order for us to compare contact times, the depth of the eclipse, and the shape of the lightcurve.
+Fortunately, Dr. Scott Austin used the UCA observatory across the street from our location to livestream the eclipse using a solar filter-equipped camera mounted to the observatory telescope.
 Another experiment near our location led by Dr. Todd Abel and UCA Student Shane Ayotte used a Vernier Light Sensor (LS-BTA) pointed straight up at the sky to measure overall sky brightness.
@@
 We accomplished this by first grayscaling the image of the eclipse and then using Otsu thresholding to only count pixels above a certain value.
-This sucessfully counts the bright sun pixels while ignoring the background noise.
+This sucessfully counted the bright sun pixels while ignoring the background noise.
 To get the time for each data point, we took an image of the in-video clock at the same time we counted the pixels of the eclipse and used computer vision to recognise the characters in the clock, giving us the time at which the frame was pixel-counted.

### 2025-03-15 sections/abstract.tex
Wording change

@@
-We present radio telescope observations of the 08 April 2024 total solar eclipse from the University of Central Arkansas campus in Conway, Arkansas using a \unit[2.3]{m} SPIDER 230C parabolic radio telescope tuned to a frequency of \unit[1420]{MHz}.
+We present radio telescope observations of the April 8th, 2024 total solar eclipse from the University of Central Arkansas campus in Conway, Arkansas using a \unit[2.3]{m} SPIDER 230C parabolic radio telescope tuned to a frequency of \unit[1420]{MHz}.
 Observations began approximately \unit[19]{min} before first contact and ended approximately \unit[2.5]{min} after fourth contact, continuously tracking the sun across the sky.

### 2025-03-15 sections/observations.tex
15X5 lightcurve figure
Tight Layout change
scaling figures to 0.93/textwidth
Spell check and commas

@@
 \begin{figure}[h]
-    \includegraphics[width=0.6\textwidth]{figures/LightcurveComparison.pdf}
+    \includegraphics[width=0.93\textwidth]{figures/LightcurveComparison.pdf}
     \caption{\label{fig:LightcurveComparison} A comparison of the smoothed/normalized radio lightcurve, the normalized optical lightcurve generated from the livestream, the lightcurve generated from the light sensor, and a theoretical lightcurve generated from the software \texttt{Stellarium}.}
@@
 Fortunately, Dr. Scott Austin used the UCA observatory across the street from our location to livestream the eclipse using a solar filter-equipped camera mounted to the observatory telescope.
-Another experiment near our location led by Dr. Todd Abel and UCA Student Shane Ayotte used a Vernier Light Sensor (LS-BTA) pointed straight up at the sky to measure overall sky brightness.
+Another experiment near our location, led by Dr. Todd Abel and UCA Student Shane Ayotte, used a Vernier Light Sensor (LS-BTA) pointed straight up at the sky to measure overall sky brightness.
 \paragraph{The Livestream Lightcurve}
@@
 \\
-Figure \ref{fig:LightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}\cite{zotti_simulated_2020}, we observed that all three had a very similar shape, with heavy overlap between the theoretical and livestream lightcurves.
+Figure \ref{fig:LightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}\cite{zotti_simulated_2020}, where we observed that all three had a very similar shape with heavy overlap between the theoretical and livestream lightcurves.
 This implies that our lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun's radio emission.

### 2025-03-15 sections/theoretical.tex
scaling figures to 0.93/textwidth
Spell check and commas

@@
 We used the free, open-source planetarium software \texttt{Stellarium}\cite{zotti_simulated_2020} to achieve this.
-After setting the time, date and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
+After setting the time, date, and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
 The resulting theoretical lightcurve was then overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
@@
 \begin{figure}
-  \includegraphics[width=0.6\textwidth]{figures/RadiovsTheoretical}
+  \includegraphics[width=0.93\textwidth]{figures/RadiovsTheoretical}
   \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}

### 2025-03-15 sections/abstract.tex
Editing the abstract wording to flow better

@@
 This contrasts with optical data, where the eclipse was total.
-To determine the relative size of the radio solar disk, we compared our observed radio and optical data with theoretical curves where we varied the solar radius.
+To determine the relative size of the radio solar disk, we compared our observed radio and optical data to theoretical lightcurves of the eclipse with different solar radii.
 From our analyses, we found that the radio solar disk is approximately $R_{\mathrm{1420}} = 1.27 R_{\odot}$.

### 2025-03-15 sections/introduction.tex
Un-capitalizing total solar eclipse

@@
-Our goal with this project is to determine the size of the sun in the radio frequency by using observations during the April 8th, 2024 Total Solar Eclipse.
+Our goal with this project is to determine the size of the sun in the radio frequency by using observations during the April 8th, 2024 total solar eclipse.
 Our radio telescope is specifically focused on the electron spin-flip transition of Hydrogen, which is observed at 1420MHz.

### 2025-03-15 sections/observations.tex
Editing the tenses in the observations section, mentioning vertical lines in the figures

@@
 \paragraph{Linear Adjustment function}
-The first step in our data analysis is to correct for the tracking error caused by re-targeting the telescope after the gust of wind.
-In our raw radio data, the brightness of the sun after fourth contact is less than the same period just before first contact.
+The first step in our data analysis was to correct for the tracking error caused by re-targeting the telescope after the gust of wind.
+In our raw radio data, the brightness of the sun after fourth contact was less than the same period just before first contact.
 This indicated that the tracking had become inaccurate.
@@
     \includegraphics[width=0.93\textwidth]{figures/LightcurveComparison.pdf}
-    \caption{\label{fig:LightcurveComparison} A comparison of the smoothed/normalized radio lightcurve, the normalized optical lightcurve generated from the livestream, the lightcurve generated from the light sensor, and a theoretical lightcurve generated from the software \texttt{Stellarium}.}
+    \caption{\label{fig:LightcurveComparison} A comparison of the smoothed/normalized radio lightcurve, the normalized optical lightcurve generated from the livestream, the lightcurve generated from the light sensor, and a theoretical lightcurve generated from the software \texttt{Stellarium}.
+Vertical lines show first through fourth contact.}
 \end{figure}
@@
 Scott Austin using a Sony Alpha 6400 camera with a Sony FE 24mm-240mm f/3.5-6.3 lens and NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter.
-This solar filter was removed during totality, marked by 2460409.2849 JD and 2460409.2884 JD.
+This solar filter was removed during totality, marked by vertical lines at 2460409.2849 JD and 2460409.2884 JD.
 This setup was attached to a Meade-14 LX200R on a Paramount MX+ equatorial mount to track the sun across the sky.

### 2025-03-15 sections/observations.tex
Specifying that we're talking about the optical ightcurves

@@
 \\
-Figure \ref{fig:LightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}\cite{zotti_simulated_2020}, where we observed that all three had a very similar shape with heavy overlap between the theoretical and livestream lightcurves.
-This implies that our lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun's radio emission.
+Figure \ref{fig:LightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}\cite{zotti_simulated_2020}, where we observed that all three optical lightcurves had a very similar shape with heavy overlap between the theoretical and livestream lightcurves.
+This implies that our optical lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun's radio emission.

### 2025-03-15 sections/observations.tex
Removing linear adjustment function
I removed the linear adjustment function to save space - I think
since we're not showing the line of the linear adjustment function
on Figure 1 anymore, we can save space by removing the equation.

This frees up some space to expand Figure 2 and make the geometrtical
relations clearer

@@
 To create this error correction function, we found the slope between a point around 2 minutes before 1st contact and a point around 2 minutes after 4th contact. 
-The sign was then flipped on the slope and combined with the x value of the point at 1st contact in point slope form in Equation \ref{linear_adjustment_function}.
-This function is added to the lighturve to adjust for the tracking error.
-\begin{equation}\label{linear_adjustment_function}
-Y = 128.4(t-2460409.2318317825)
-\end{equation}
-Where $Y$ is the adjustment value and $t$ is the time coordinate of each data point. 
+The sign was then flipped on the slope and combined with the x value of the point at 1st contact in point slope form.
+This function was added to the lighturve to adjust for the tracking error.
+%\begin{equation}\label{linear_adjustment_function}
+%Y = 128.4(t-2460409.2318317825)
+%\end{equation}
 \paragraph{Smoothing}

### 2025-03-15 sections/theoretical.tex
Expanding the geomery figure

@@
 
-To determine the apparent radius of the sun at \unit[1420]{MHz}, we can compare our observed radio lightcurve to a series of theoretical lightcurves where the radius of the sun has been changed.
+To determine the apparent radius of the sun at \unit[1420]{MHz}, we compared our observed radio lightcurve to a series of theoretical lightcurves where the radius of the sun has been changed.
 To accomplish this, we first downloaded high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}. 
@@
 \begin{minipage}{0.49\textwidth}
-  \includegraphics[width=0.6\textwidth]{figures/drawing_updated}
+  \includegraphics[width=0.75\textwidth]{figures/drawing_updated}
   \caption{\label{fig:eclipse_geometry} The geometric relationships used to calculate the obscuration of the sun.
@@
   \includegraphics[width=0.93\textwidth]{figures/RadiovsTheoretical}
-  \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}
+  \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.
+Our best fit to the depth of the radio lightcurve has an apparent solar radius of $1.27 R_{\odot}$}
 \end{figure}

### 2025-03-15 sections/introduction.tex
changed these to this

@@
 We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
-In order to compare the radio lightcurve with the visual one, we have two sources of optical lightcurve data: a livestream from the UCA Observatory and a broad-spectrum light sensor pointed at the sky.
-We also generated theoretical lightcurves using the software Stellarium \cite{zotti_simulated_2020} and the JPL Horizons On-Line Ephemeris System \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}.
-Using these data, we can compare the optical and radio lightcurves to determine the relative size of the radio solar disk.
+In order to compare the radio eclipse to the optical eclipse, we have two sources of optical lightcurve data: a livestream from the UCA Observatory and a broad-spectrum light sensor pointed at the sky.
+We also generated theoretical lightcurves using the software \texttt{Stellarium}\cite{zotti_simulated_2020} and the JPL Horizons On-Line Ephemeris System \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}.
+Using this data, we can compare the optical and radio lightcurves to determine the relative size of the radio solar disk.

### 2025-03-15 sections/acknowledgements.tex

@@
 
-Our research team practices open-source science.
-All data and analysis code can be accessed at \url{https://github.com/UCA-Open-Astronomy-Lab/total_solar_eclipse}.
-The repository for this paper can be found at \url{https://github.com/UCA-Open-Astronomy-Lab/jurpa_eclipse_paper}
+Our research team practices open-source science. All data and analysis code, along with the source of this paper can be accessed at \url{https://github.com/UCA-Open-Astronomy-Lab}
 
-This research would not have been possible without the support of state and federal research grants.
+This research would not have been possible without the support of state and federal grants.
 Funding to purchase the radio telescope came from the Arkansas Space Grant Consortium (ASGC) Statewide Equipment Award, matched by ASGC state match 20-ARMF-02.
 Funding to support student research and travel to present our results came from the ASGC Student Intensive Training award.
-These ASGC awards are subawards of NASA award number 80NSSC20M0106.
+These ASGC awards are subawards of NASA award 80NSSC20M0106.

### 2025-03-15 sections/conclusion.tex

--- 2025-03-11 sections/conclusion.tex
@@
 This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$, falling between the results of other studies \cite{messerotti_radio_2000} and \cite{leung_solar_2022}.
-In future work, we hope to examine the radio lightcurve in detail, with the goal of mapping radio emission from the sun's surface as features are eclipsed by the moon's edge moving across the face of th sun, as done in \cite{messerotti_radio_2000}.
+In future work, we hope to examine the radio lightcurve in detail with the goal of mapping radio emission from the sun's surface as features are eclipsed by the moon's edge moving across the face of the sun, as done in \cite{messerotti_radio_2000}.

### 2025-05-11 sections/observations.tex
added a reference to otsu thresholding

@@
 To transform the livestream into a lightcurve, we needed to extract the percentage of the sun's disk visible in the video frames as the eclipse progressed.
-We accomplished this by first grayscaling the image of the eclipse and then using Otsu thresholding to only count pixels above a certain value.
+We accomplished this by first grayscaling the image of the eclipse and then using Otsu thresholding \cite{otsu_1979} to only count pixels above a certain value.
 This sucessfully counted the bright sun pixels while ignoring the background noise.

### 2025-05-12 response.tex
Adding response file

\documentclass{article}
\begin{document}

We are greatful to the reviewer for their insightful suggestions to improve our manuscript.
Included below are summaries of the reviewer's suggested changes, and our modifications to the manuscript.

\section{Savitsky-Golay filtering}

From the reviewer:

\begin{quote}
The authors also use a well-tested filtering method for accounting for interference.
I am curious, though, why was this method chosen over others? I suspect it may be that it is straightforward, which reduces the possibility of introducing more errors and biases, but it is not clear.
\end{quote}
\noindent We have added the following:

\begin{quote}
  \input{sections/savitsky_golay.tex}
\end{quote}

\end{document}

### 2025-05-12 response.tex
Adding the Otsu reference to the response document

@@
 We are greatful to the reviewer for their insightful suggestions to improve our manuscript.
-Included below are summaries of the reviewer's suggested changes, and our modifications to the manuscript.
+Included below are the the reviewer's suggested changes, and our modifications to the manuscript.
 
@@
 \end{quote}
-\noindent We have added the following:
+\noindent We have added the following to our description of the filtering method used:
 
@@
 
+\section{Wind gust}
+
+From the reviewer:
+
+\begin{quote}
+  Although a ``gust of wind'' is mentioned, it is not clearly indicated in the data when that gust occurred, so it would be helpful to point that out if the timing is known.
+\end{quote}
+
+\noindent To address this issue, we have modified the caption of Figure 1 to indicate the timing of the wind gust:
+
+\begin{quote}
+  \input{sections/wind.tex}
+\end{quote}
+
+\noindent From the reviewer:
+
+\begin{quote}
+  Although something like that may not be possible to correct in the data analysis, it may be worth re-mentioning in the discussion where the radio light curve is compared to the theoretical curve.
+\end{quote}
+
+\noindent Because the wind gust occurred before the radio and optical lightcurves began to diverge, we have opted not to include further discussion of the wind gust in our comparison with theoretical lightcurves.
+
+\section{Otsu thresholding}
+
+From the reviewer:
+
+\begin{quote}
+  I would suggest, however, including a reference or very brief definition of Otsu thresholding.
+\end{quote}
+
+\noindent We have included the following reference: N. Otsu, “A threshold selection method from gray-level histograms,” IEEE Transactions on Systems, Man, and Cybernetics 9, 62–66 (1979)
+
 \end{document}

### 2025-05-12 response.tex
Addressing model matching and why we chose sources

@@
 \documentclass{article}
+\usepackage{units}
 \begin{document}
@@
 
+\section{Model matching}
+
+From the reviewer:
+
+\begin{quote}
+  It is not clear if the ``best fit curve'' was determined numerically or by eye
+\end{quote}
+
+\noindent The model was fit ``by eye.'' The following is not included in the theoretical lightcurve comparison section:
+
+\begin{quote}
+  \input{sections/model_matching.tex}
+\end{quote}
+
+From the reviewer:
+
+\begin{quote}
+
+  The variance in slope is particularly interesting! Is this also seen elsewhere in the literature?
+
+\end{quote}
+
+\noindent We have modified the conclusion as follows:
+
+\begin{quote}
+  \input{sections/model_slope.tex}
+\end{quote}
+
+\section{Comparison with other works}
+
+From the reviewer:
+
+\begin{quote}
+  It is not clear why References 4 and 5 were chosen as the only reference points.
+  I suspect it is because they were also measured at 1420 MHz and during a solar eclipse. If this is the case, it should be stated.
+\end{quote}
+
+\noindent We have included the following to the theoretical lightcurve comparison section
+
+\begin{quote}
+  \input{sections/comparison_sources.tex}
+\end{quote}
+
+\bibliography{refs}% Produces the bibliography via BibTeX.
+\bibliographystyle{plain}
+
 \end{document}

### 2025-05-12 sections/model_slope.tex
Addressing model matching and why we chose sources

In future work, we hope to examine the radio lightcurve in detail with the goal of analyzing the variance seen between our model slope and the recorded radio data. In a previous study by \cite{messerotti_radio_2000} the slopes also differ, but not to the degree seen in our data.
In \cite{messerotti_radio_2000}, that variance is used to map radio emission from the sun's surface as features are eclipsed by the moon's edge moving across the face of the sun, something we hope to replicate in a future study.

### 2025-05-12 sections/theoretical.tex
Addressing model matching and why we chose sources

@@
 \begin{equation}\label{eq:geometry_1}
-  A_1 = \frac{1}{2}r_{\odot}^2\left(\phi_1 - \sin\phi_1\right)
+  A_1 = \frac{1}{2}R_{\odot}^2\left(\phi_1 - \sin\phi_1\right)
 \end{equation}
 \begin{equation}\label{eq:geometry_2}
-  A_2 = \frac{1}{2}r_{m}^2\left(\phi_2 - \sin\phi_2\right)
+  A_2 = \frac{1}{2}R_{m}^2\left(\phi_2 - \sin\phi_2\right)
 \end{equation}
 \begin{equation}\label{eq:geometry_3}
-  \phi_1 = 2\cos^{-1}\left(\frac{r_{\odot}^2 - r_{m}^2+x^2}{2r_{\odot}x}\right)
+  \phi_1 = 2\cos^{-1}\left(\frac{R_{\odot}^2 - R_{m}^2+x^2}{2R_{\odot}x}\right)
 \end{equation}
 \begin{equation}\label{eq:geometry_4}
-  \phi_2 = 2\cos^{-1}\left(\frac{x^2 - r_{\odot}^2 + r_{m}^2}{2r_{m}x}\right)
+  \phi_2 = 2\cos^{-1}\left(\frac{x^2 - R_{\odot}^2 + r_{m}^2}{2R_{m}x}\right)
 \end{equation}
@@
 Using these relationships, we were able to create theoretical lightcurves for varying solar radii from $R = 1.0 R_{\odot}$ to $R = 1.45 R_{\odot}$.
+\input{sections/model_matching.tex}
 These theoretical lightcurves, shown in Figure \ref{fig:RadiovsTheoretical}, helped us match the dip in relative brightness within the radio lightcurve, but it was not a perfect match.
@@
 This lies between the results of $R_{\mathrm{1420}} = 1.14 R_{\odot}$ found by \cite{messerotti_radio_2000}, and $R_{\mathrm{1420}} = 1.4 R_{\odot}$ found by \cite{leung_solar_2022}.
+\input{sections/comparison_sources.tex}

### 2025-05-12 response.tex
Comparing with historical observations

@@
 
-From the reviewer:
+\noindent From the reviewer:
 
@@
 
-\noindent We have included the following to the theoretical lightcurve comparison section
+\noindent We have included the following to the theoretical lightcurve comparison section:
 
@@
   \input{sections/comparison_sources.tex}
+\end{quote}
+
+\noindent From the reviewer:
+
+\begin{quote}
+  The authors should also consider comparing it to the long history of measurements of solar radii at radio wavelengths through other methods, such as those listed in Menezes \& Valio (2018).
+  Does this measurement fit the general trend of radius with frequency?
+\end{quote}
+
+\noindent We have added the following to our comparision with other works:
+
+\begin{quote}
+  \input{sections/history.tex}
+\end{quote}
+
+\section{Emission source}
+
+\noindent From the reviewer:
+
+\begin{quote}
+  Finally, indicate, perhaps in the introduction or discussion, what kind of emission IS being given off in the radio that gives us this larger radius?
+(It’s not from the blackbody spectrum that dominates in the visible.)
 \end{quote}

### 2025-05-12 sections/introduction.tex
Adding an explanation of the emission mechanism

@@
 Our radio telescope is specifically focused on the electron spin-flip transition of Hydrogen, which is observed at 1420MHz.
+\input{sections/emission.tex}
 We collected data in both the optical and radio frequencies, providing a unique opportunity to compare the relative size in the optical and radio spectra.
@@
 We also generated theoretical lightcurves using the software \texttt{Stellarium}\cite{zotti_simulated_2020} and the JPL Horizons On-Line Ephemeris System \cite{nasa_jpl_solar_system_dynamics_group_jpl_nodate}.
-Using this data, we can compare the optical and radio lightcurves to determine the relative size of the radio solar disk.
+Using these data, we can compare the optical and radio lightcurves to determine the relative size of the radio solar disk.

### 2025-05-12 sections/observations.tex
justifying savitsky
Moving justification for S-G filter to its own file
Fixing mistake in path to savitsky_golay.tex
Adding the timing of the wind gust to the figure caption
removed redundant "created noise in the data."

@@
 During observation, we encountered minimal cloud cover and no sustained winds.
-Despite this, we did have 3 sources of error: A strong gust of wind pushed the telescope off target for a few seconds, an issue with the accuracy of our polar alignment caused the telescope to be slightly off target by the end of observation, and local sources of interference created noise in the data.
+Despite this, we did have 3 sources of error: A strong gust of wind pushed the telescope off target for a few seconds, an issue with the accuracy of our polar alignment caused the telescope to be slightly off target by the end of observation, and local sources of interference.
 In order for this raw data to be compared to the optical lightcurve, these errors must be addressed.
@@
 We chose to apply a Savitzky-Golay filter \cite{savitzky_golay_1964} to do this.
+\input{sections/savitsky_golay.tex}
+
 \paragraph{Normalization}
@@
     \caption{\label{fig:LightcurveComparison} A comparison of the smoothed/normalized radio lightcurve, the normalized optical lightcurve generated from the livestream, the lightcurve generated from the light sensor, and a theoretical lightcurve generated from the software \texttt{Stellarium}.
-Vertical lines show first through fourth contact.}
+Vertical lines show first through fourth contact.
+\protect\input{sections/wind.tex}}
 \end{figure}

### 2025-05-12 sections/introduction.tex
Re-wording the introduction to make the tuning and emission clear
We dont' need to mention Hydrogen, since that's not what we're
observing. The emission mechanism also lets us explain up-front why
the sun would appear larger at radio frequencies.

@@
-Our goal with this project is to determine the size of the sun in the radio frequency by using observations during the April 8th, 2024 total solar eclipse.
-Our radio telescope is specifically focused on the electron spin-flip transition of Hydrogen, which is observed at 1420MHz.
+Our goal with this project is to determine the apparent size of the sun using \unit[1420]{MHz} radio telescope observations during the April 8th, 2024 total solar eclipse.
 \input{sections/emission.tex}

### 2025-05-12 sections/observations.tex
punctuation
Tighten up description of radio telescope and data analysis methods

@@
 We began collecting data at 2460409.2186657293 JD and ended at 2460409.3424835186 JD, or 2024-04-08 17:14:53 UTC and 2024-04-08 20:13:11 UTC.
-The telescope used was a Spider 230C radio telescope with a 2.3 m parabolic dish tuned to the electron spin-flip transition of Hydrogen at 1420 MHz.
+The telescope used was a Spider 230C radio telescope with a 2.3 m parabolic dish tuned to 1420 MHz.
 During observation, we encountered minimal cloud cover and no sustained winds.
 Despite this, we did have 3 sources of error: A strong gust of wind pushed the telescope off target for a few seconds, an issue with the accuracy of our polar alignment caused the telescope to be slightly off target by the end of observation, and local sources of interference.
-In order for this raw data to be compared to the optical lightcurve, these errors must be addressed.
-A number of data analysis methods were used to do this:
+A number of data analysis methods were used to address these errors
 \paragraph{Linear Adjustment function}
@@
 Vertical lines show first through fourth contact.
-\protect\input{sections/wind.tex}}
+\protect\input{sections/wind.tex}.}
 \end{figure}

### 2025-05-12 sections/observations.tex
Removing the first... second... third... language in the data analysis
We can cut this to save space, and the italisized pararaph titles
will maintain clarity for each step

@@
 Despite this, we did have 3 sources of error: A strong gust of wind pushed the telescope off target for a few seconds, an issue with the accuracy of our polar alignment caused the telescope to be slightly off target by the end of observation, and local sources of interference.
-A number of data analysis methods were used to address these errors
+A number of data analysis methods were used to address these errors:
 \paragraph{Linear Adjustment function}
-The first step in our data analysis was to correct for the tracking error caused by re-targeting the telescope after the gust of wind.
 In our raw radio data, the brightness of the sun after fourth contact was less than the same period just before first contact.
@@
 \paragraph{Smoothing}
-The next step is to smooth the data.
 Our choice to smooth the data came from the need to reduce noise/random spikes in the data to get a better idea of the shape of the curve.
@@
 \paragraph{Normalization}
-The final step is to normalize the data.
 Normalization is the process by which the data of a graph is scaled by a constant such that the highest points are equal to 100, essentially making the data a percentage of its highest value.

### 2025-05-12 sections/observations.tex
Fix spelling mistakes, shrink graphs a bit

@@
 The sign was then flipped on the slope and combined with the x value of the point at 1st contact in point slope form.
-This function was added to the lighturve to adjust for the tracking error.
+This function was added to the lightcurve to adjust for the tracking error.
 %\begin{equation}\label{linear_adjustment_function}
@@
 \begin{figure}[h]
-    \includegraphics[width=0.93\textwidth]{figures/LightcurveComparison.pdf}
+    \includegraphics[width=0.9\textwidth]{figures/LightcurveComparison.pdf}
     \caption{\label{fig:LightcurveComparison} A comparison of the smoothed/normalized radio lightcurve, the normalized optical lightcurve generated from the livestream, the lightcurve generated from the light sensor, and a theoretical lightcurve generated from the software \texttt{Stellarium}.
@@
 Because the light sensor data had timestamps included, we used it to confirm the timing accuracy of our other lightcurves.
-\\
+
 Figure \ref{fig:LightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}\cite{zotti_simulated_2020}, where we observed that all three optical lightcurves had a very similar shape with heavy overlap between the theoretical and livestream lightcurves.

### 2025-05-12 sections/theoretical.tex
Mentioned other variances in slope from reference papers.
Comparing with historical observations
Cleaning up duplicate changes
punctuation
Shrink figures a bit, tighten up wording

@@
 The resulting theoretical lightcurve was then overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
-The agreement between the two is excellent, as shown in Figure \ref{fig:LightcurveComparison}, validating our optical eclipse lightcurve.
+The agreement between the two is excellent, as shown in Figure \ref{fig:LightcurveComparison}.
 
@@
 \begin{minipage}{0.49\textwidth}
-  \includegraphics[width=0.75\textwidth]{figures/drawing_updated}
+  \includegraphics[width=0.65\textwidth]{figures/drawing_updated}
   \caption{\label{fig:eclipse_geometry} The geometric relationships used to calculate the obscuration of the sun.
-The percent obscuration is found by dividing the combined area $A_1 + A_2$ by the apparent area of the sun's disk $\pi R_\odot^2$}
+The percent obscuration is found by dividing the combined area $A_1 + A_2$ by the apparent area of the sun's disk $\pi R_\odot^2$.}
 \end{minipage}
@@
 \begin{figure}
-  \includegraphics[width=0.93\textwidth]{figures/RadiovsTheoretical}
+  \includegraphics[width=0.9\textwidth]{figures/RadiovsTheoretical}
   \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.
@@
 \input{sections/comparison_sources.tex}
+
+\input{sections/history.tex}

### 2025-05-12 sections/observations.tex
Spelling fixes

@@
 We accomplished this by first grayscaling the image of the eclipse and then using Otsu thresholding \cite{otsu_1979} to only count pixels above a certain value.
-This sucessfully counted the bright sun pixels while ignoring the background noise.
-To get the time for each data point, we took an image of the in-video clock at the same time we counted the pixels of the eclipse and used computer vision to recognise the characters in the clock, giving us the time at which the frame was pixel-counted.
+This successfully counted the bright sun pixels while ignoring the background noise.
+To get the time for each data point, we took an image of the in-video clock at the same time we counted the pixels of the eclipse and used computer vision to recognize the characters in the clock, giving us the time at which the frame was pixel-counted.
 The number of pixels of the solar disk over time can then be normalized to a relative brightness.

### 2025-05-12 sections/theoretical.tex
Tightening up language

@@
 \input{sections/model_matching.tex}
-These theoretical lightcurves, shown in Figure \ref{fig:RadiovsTheoretical}, helped us match the dip in relative brightness within the radio lightcurve, but it was not a perfect match.
-Although the dip in brightness was accurate, the curves show variance in slope and our radio data does not show the flat bottom expected while the moon transits the larger solar disk.
+These theoretical lightcurves are compared with the radio lightcurve in Figure \ref{fig:RadiovsTheoretical}.
+Although our best-fit model matches the observed dip in brightness, it fails to match the slope of the observed lightcurve before and after totality, and does not show the flat bottom expected while the moon transits the larger solar disk.
 The theoretical curves assume a uniform disk brightness, not accounting for limb darkening, sunspots, radio emission from the corona, or other solar activity.

### 2025-05-14 sections/acknowledgements.tex
Shortening titles in acknowledgements

@@
 \noindent Special thanks to Scott Austin, Ph.D.
-(Director of Astronomical Facilities, Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas), Todd Abel, Ph.D.
-(UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator), and Shane Ayotte (UCA Mathematics Student).
+(Associate Professor of Astronomy and Physics, UCA), Todd Abel, Ph.D.
+(UCA STEM Institute Co-Director, Associate Professor of Mathematics), and Shane Ayotte (UCA Mathematics Student).
 

### 2025-05-14 sections/acknowledgements.tex
Making acknowledgements section shorter

@@
 (UCA STEM Institute Co-Director, Associate Professor of Mathematics), and Shane Ayotte (UCA Mathematics Student).
-
-Our research team practices open-source science. All data and analysis code, along with the source of this paper can be accessed at \url{https://github.com/UCA-Open-Astronomy-Lab}
-
-This research would not have been possible without the support of state and federal grants.
-Funding to purchase the radio telescope came from the Arkansas Space Grant Consortium (ASGC) Statewide Equipment Award, matched by ASGC state match 20-ARMF-02.
-Funding to support student research and travel to present our results came from the ASGC Student Intensive Training award.
+All data and analysis code, along with the source of this paper can be accessed at \url{https://github.com/UCA-Open-Astronomy-Lab}.
+Funding for this research came from an Arkansas Space Grant Consortium (ASGC) Statewide Equipment Award, and an ASGC Student Intensive Training award.
 These ASGC awards are subawards of NASA award 80NSSC20M0106.

### 2025-05-14 sections/observations.tex
Changed wording of smoothing section to get us back to 4 pages

@@
 \paragraph{Smoothing}
-Our choice to smooth the data came from the need to reduce noise/random spikes in the data to get a better idea of the shape of the curve.
+Our choice to smooth the data came from the need to reduce noise/random spikes and get a better idea of the shape of the curve.
 We chose to apply a Savitzky-Golay filter \cite{savitzky_golay_1964} to do this.

### 2025-05-14 sections/observations.tex
secondary citation of stellarium

@@
 
-Figure \ref{fig:LightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}\cite{zotti_simulated_2020}, where we observed that all three optical lightcurves had a very similar shape with heavy overlap between the theoretical and livestream lightcurves.
+Figure \ref{fig:LightcurveComparison} shows the observed lightcurves and a theoretical lightcurve generated from the software \texttt{Stellarium}, where we observed that all three optical lightcurves had a very similar shape with heavy overlap between the theoretical and livestream lightcurves.
 This implies that our optical lightcurves are accurate and can be used to compare with our radio lightcurve to determine the size of the sun's radio emission.

### 2025-05-14 sections/conclusion.tex
Addressing model matching and why we chose sources
hypothesis to expectation

@@
-Based on our comparison of data from a 2.3 m radio telescope, a broad-spectrum light sensor, an optical livestream, and theoretical data from \texttt{Stellarium} and JPL Horizons, our hypothesis that the radio solar disk is larger than the optical solar disk is supported.
+Based on our comparison of data from a 2.3 m radio telescope, a broad-spectrum light sensor, an optical livestream, and theoretical data from \texttt{Stellarium} and JPL Horizons, our expectation that the radio solar disk is larger than the optical solar disk is supported.
 This analysis found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$, falling between the results of other studies \cite{messerotti_radio_2000} and \cite{leung_solar_2022}.
-In future work, we hope to examine the radio lightcurve in detail with the goal of mapping radio emission from the sun's surface as features are eclipsed by the moon's edge moving across the face of the sun, as done in \cite{messerotti_radio_2000}.
+\input{sections/model_slope.tex}

### 2025-05-14 sections/observations.tex
Renamed figures and applied changes to tex files
local sources of noise expanded upon

@@
 During observation, we encountered minimal cloud cover and no sustained winds.
-Despite this, we did have 3 sources of error: A strong gust of wind pushed the telescope off target for a few seconds, an issue with the accuracy of our polar alignment caused the telescope to be slightly off target by the end of observation, and local sources of interference.
+Despite this, we did have 3 sources of error: A strong gust of wind pushed the telescope off target for a few seconds, an issue with the accuracy of our polar alignment caused the telescope to be slightly off target by the end of observation, and local sources of interference introduced noise into the signal.
 A number of data analysis methods were used to address these errors:
@@
 \begin{figure}[h]
-    \includegraphics[width=0.9\textwidth]{figures/LightcurveComparison.pdf}
+    \includegraphics[width=0.9\textwidth]{figures/Figure1.pdf}
     \caption{\label{fig:LightcurveComparison} A comparison of the smoothed/normalized radio lightcurve, the normalized optical lightcurve generated from the livestream, the lightcurve generated from the light sensor, and a theoretical lightcurve generated from the software \texttt{Stellarium}.
